---
title: "Trade-offs meta-analysis results"
author: ""
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#kniter setting
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE, # no warnings
cache = TRUE,# Cacheing to save time when kniting
tidy = TRUE
)

# clear work space
rm(list=ls())

options(digits=2)

#Set working directory to location of this script. This will work for anyone. So there is no need to change any of the directory-related codes in the script.

 dir.name <- dirname(rstudioapi::getActiveDocumentContext()$path)
 setwd(dir.name)
 getwd()
# 
# #Check that you are in the right directory by looking at the files in the folder
# list.files()
```

```{r loadpackages, echo = FALSE, results = "hide", messages = FALSE}
# to install orchaRd pacakge

# install.packages("devtools")
# install.packages("tidyverse")
#remotes::install_github("wviechtb/metafor")
# install.packages("patchwork")
# install.packages("R.rsp")
#devtools::install_github("daniel1noble/orchaRd", force = TRUE, build_vignettes = TRUE)
#remotes::install_github("rvlenth/emmeans", dependencies = TRUE, build_opts = "") 
#devtools::install_github("kupietz/kableExtra")
#install ggtherm
#devtools::install_github('cttobin/ggthemr')

# Install ggtree:
#install.packages("BiocManager")
#library(BiocManager)
#BiocManager::install("ggtree")
#Load required packages.

pacman::p_load(tidyverse, #Tidy family and related packages
               metafor, #Meta-analysis package
               readxl, #Reading excel .xlsx files
               MuMIn, #Model selection and averaging package
               viridis, #Nice colours that are colour blind friendly
               psych, #Some useful features like correlational analyses
               rotl, #Open tree of life for phylogenetic tree making
               ape, #For phylogenetic analysis
               kableExtra, #For making nice tables
               orchaRd, #Functions for I^2 and R^2
               here, #Easy file path reference
               clubSandwich, #Robust error variance estimator
               GoodmanKruskal, #Associations between categorical variables
               emmeans, #Estimated marginal means
               esc, #Some useful effect size calculations
               patchwork, #Plotting multiple plots in one figure
               effectsize, ##Some useful effect size calculations
               estmeansd, #Estimating mean and sd from quantiles
               flextable, #Making tables
               cowplot, #Plotting add-on for ggplot
               magick, #Read images and insert as figures in knitted document
               ggthemr,
               rphylopic,
               ggtree,
               ggtreeExtra,
               ggnewscale)


# getting functions functions
source("effect_function.R", chdir = TRUE)
```

```{r upload dataset, echo = FALSE, results = "hide", messages = FALSE}
#Load dataset
data <- read_xlsx(here("dataset.xlsx"), 
                  sheet = "data",
                  na="") %>% 
  mutate_if(is.character, as.factor) #Classify variable as a factor if it is a character

str(data)

data <- data %>% 
  mutate(direction_immune_reprod=paste0(immunity_direction, "_", reproduction_direction)) %>% 
  mutate(reverse=case_when(
    direction_immune_reprod=="positive_positive"~"no",
    direction_immune_reprod=="negative_negative"~"no",
    direction_immune_reprod=="positive_negative"~"yes",
    direction_immune_reprod=="negative_positive"~"yes"))
```

```{r subset SMD dataset, echo = FALSE, results = "hide", messages = FALSE}
#Subsetting data by the stats that was recorded so that we can apply the appropriate formula to calculate the effect size and then combine them again into a single dataset

#subset the experimental studies
data_exp <- data[data$correlational_experimental == "experimental",]

#subset only the rows with descriptive effects
data_exp_mean <- data_exp[data_exp$stats == "mean",]

#convert dispersion stats to sd
data_exp_mean <- data_exp_mean %>% 
  mutate(sdcontrol=case_when(
  dispersion_stats=="sd"~dispersion_control,
  dispersion_stats=="se"~dispersion_control*sqrt(n_control),
  dispersion_stats=="IQ"~dispersion_control/1.35))

data_exp_mean <- data_exp_mean %>%
  mutate(sdexperimental=case_when(
    dispersion_stats=="sd"~dispersion_experimental,
    dispersion_stats=="se"~dispersion_experimental*sqrt(n_experimental),
    dispersion_stats=="IQ"~dispersion_experimental/1.35))

#subset only the rows with proportion data
data_exp_prop <- data_exp[data_exp$stats == "count"| data_exp$stats == "proportion",]

#Calculate both success proportions and counts
data_exp_prop <- data_exp_prop %>%
  mutate(successtreatment=case_when(
    stats=="proportion"~success_experimental*n_experimental,
    stats=="count"~success_experimental)) %>%
  mutate(successctrl=case_when(
    stats=="proportion"~success_control*n_control,
    stats=="count"~success_control))

data_exp_prop <- data_exp_prop %>%
  mutate(propsuccesstreatment=case_when(
    stats=="proportion"~success_experimental,
    stats=="count"~success_experimental/n_experimental)) %>%
  mutate(propsuccessctrl=case_when(
    stats=="proportion"~success_control*n_control,
    stats=="count"~success_control/n_control))

#subset only the rows with Cohen's d
data_exp_cohen <- data_exp[data_exp$stats == "Cohen",]

#subset only the rows with Regression t value
data_exp_t <- data_exp[data_exp$stats == "t",]
```

```{r subset cor dataset, echo = FALSE, results = "hide", messages = FALSE}
#subset the correlational studies
data_cor <- data[data$correlational_experimental == "correlational",]

#subset only the rows with correlation data
data_cor_r <- data_cor[data_cor$stats == "r",]

#subset only the rows with proportion data
data_cor_prop <- data_cor[data_cor$stats == "count",]

#subset only the rows with mean data
data_cor_mean <- data_cor[data_cor$stats == "mean",]

#subset only the rows with r2 data
data_cor_r2 <- data_cor[data_cor$stats == "r2",]

#subset only the rows with F data
data_cor_F <- data_cor[data_cor$stats == "F",]

#subset only the rows with median data
data_cor_median <- data_cor[data_cor$stats == "median",]

#subset only the rows with regt data
data_cor_regt <- data_cor[data_cor$stats == "t",]
```

```{r escalc SMD, echo = FALSE, results = "hide", messages = FALSE}
#Calculate effect size for SMD. 
SMD_descstats <- escalc(data = data_exp_mean, measure = "SMD", 
                n2i = n_control, n1i = n_experimental,
                m2i = value_control, m1i = value_experimental,
                sd2i = sdcontrol, sd1i = sdexperimental)


SMD_prop <- escalc(data = data_exp_prop,
                   measure = "PBIT", 
                   ai=successtreatment,
                   n1i=n_experimental,
                   ci=successctrl,
                   n2i=n_control
                   )

SMD_regt <- data_exp_t %>% 
  mutate(yi=((t*(n_experimental+n_control))/((sqrt(n_experimental*n_control))*(sqrt(df))))) %>% 
  mutate(vi=(((n_experimental+n_control)/(n_experimental*n_control))+((yi*yi)/(2*(n_experimental+n_control-2)))))

SMD_cohend <- escalc(data = data_exp_cohen, measure = "SMD", 
                n2i = n_control, n1i = n_experimental,
                di = Cohen)

#Combine the separate datasets into a single SMD dataset and reverse score the relevant effect sizes
SMD <- dplyr::bind_rows(SMD_descstats,
                        SMD_prop,
                        SMD_regt,
                        SMD_cohend) %>% 
  mutate(yi=case_when(
    reverse=="yes"~yi*(-1),
    reverse=="no"~yi))
```

```{r escalc cor, echo = FALSE, results = "hide", messages = FALSE}
#Calculate effect size for correlations
cor_r <- escalc(data = data_cor_r, measure = "COR", 
                ni = n_correlation,
                ri = r)

#Calculate effect size for proportions
cor_prop <- data_cor_prop %>% 
  mutate(failure_experimental=n_experimental-success_experimental,
         failure_control=n_control-success_control) %>% 
  mutate(yi=(((success_experimental*failure_control)-(failure_experimental*success_control))/(sqrt((success_experimental+failure_experimental)*(success_control+failure_control)*(success_experimental+success_control)*(failure_experimental+failure_control))))) %>% 
  mutate(n_correlation=(n_experimental + n_control))

#Calculate effect size for means
data_cor_mean <- data_cor_mean %>% 
  mutate(sdcontrol=case_when(
  dispersion_stats=="sd"~dispersion_control,
  dispersion_stats=="se"~dispersion_control*sqrt(n_control)))

data_cor_mean <- data_cor_mean %>%
  mutate(sdexperimental=case_when(
    dispersion_stats=="sd"~dispersion_experimental,
    dispersion_stats=="se"~dispersion_experimental*sqrt(n_experimental)))

cor_mean <- data_cor_mean %>% 
  mutate(n_correlation=(n_experimental + n_control)) %>% 
  mutate(pooledsd = sqrt((((sdexperimental^2)*(n_experimental-1)) + ((sdcontrol^2)*(n_control-1)))/(n_correlation-2))) %>% 
  mutate(cohend = ((value_experimental-value_control)/(pooledsd))) %>% 
  mutate(prop_n_experimental = n_experimental/n_correlation) %>% 
  mutate(yi = (cohend)/(sqrt(cohend^2+(1/(prop_n_experimental*(1-prop_n_experimental))))))

#Calculate effect size for median
data_cor_median$q1_control<- (data_cor_median$value_control-(data_cor_median$dispersion_control/2))
data_cor_median$q3_control<- (data_cor_median$value_control+(data_cor_median$dispersion_control/2))

data_cor_median$q1_experimental<- (data_cor_median$value_experimental-(data_cor_median$dispersion_experimental/2))
data_cor_median$q3_experimental<- (data_cor_median$value_experimental+(data_cor_median$dispersion_experimental/2))

data_cor_median <- data_cor_median %>%
  drop_na("q1_control") %>% 
  rowwise() %>% 
  mutate(list_control = list(qe.mean.sd(
    q1.val = q1_control, 
    med.val = value_control, 
    q3.val = q3_control, 
    n =n_control)[c("est.mean", "est.sd")])
    ) %>% 
  unnest_wider(list_control) %>% 
  rename(est_mean_control=est.mean,
         est_sd_control=est.sd) %>% 
  rowwise() %>% 
  mutate(list_exp = list(qe.mean.sd(
    q1.val = q1_experimental, 
    med.val = value_experimental, 
    q3.val = q3_experimental, 
    n =n_experimental)[c("est.mean", "est.sd")])
    ) %>% 
  unnest_wider(list_exp) %>% 
  rename(est_mean_experimental=est.mean,
         est_sd_experimental=est.sd)

cor_median <- data_cor_median %>% 
  mutate(n_correlation=(n_experimental + n_control)) %>% 
  mutate(pooledsd = sqrt((((est_sd_experimental^2)*(n_experimental-1)) + ((est_sd_control^2)*(n_control-1)))/(n_correlation-2))) %>% 
  mutate(cohend = ((est_mean_experimental-est_mean_control)/(pooledsd))) %>% 
  mutate(prop_n_experimental = n_experimental/n_correlation) %>% 
  mutate(yi = (cohend)/(sqrt(cohend^2+(1/(prop_n_experimental*(1-prop_n_experimental))))))

#Calculate effect size for F
cor_F <- F_to_r(f=data_cor_F$F, 
                df=1, 
                df_error=data_cor_F$df, ci = 0.95)

cor_F <- as.data.frame(cor_F) %>% 
  rename(yi = r)

cor_F <- cbind(data_cor_F,cor_F) %>% 
  mutate(n_correlation = n)

#Calculate effect size for regression t
cor_regt <- data_cor_regt %>% 
  mutate(r_regt=((t)/(sqrt((t^2)+df)))) %>% 
  mutate (n_correlation = coalesce(n,n_correlation))

cor_regt <- escalc(data = cor_regt, measure = "COR", 
                ni = n_correlation,
                ri = r_regt)

#Calculate effect size for R2
cor_r2 <- data_cor_r2 %>% 
  mutate(yi = sqrt((1)-(((n_correlation-1)*(1-r2))/(n_correlation-k-1))))

cor <- dplyr::bind_rows(cor_r,
                        cor_prop,
                        cor_mean,
                        cor_regt,
                        cor_median,
                        cor_F,
                        cor_r2) %>% 
  mutate(yi=case_when(
    reverse=="yes"~yi*(-1),
    reverse=="no"~yi)) %>% 
  mutate(yi=case_when(
    esid=="es189"~yi*(-1),
    esid!= "es189"~yi))%>% 
  mutate(yi=case_when(
    esid=="es531"~yi*(-1),
    esid!= "es531"~yi))

cor_na <- cor %>% 
  filter(is.na(yi))

cor$yi_zr <- 0.5*log((1+cor$yi)/(1-cor$yi))
cor$se_zr <- 1/(sqrt(cor$n_correlation-3))

#Remove rows without effect size
cor <- cor %>% drop_na(yi_zr)
```

```{r phylogeny SMD, echo = FALSE, results = "hide", messages = FALSE,fig.show='hide'}
#Run all
taxa_smd <- tnrs_match_names(names = levels(SMD$species))
taxa_smd

#Clean species name 
SMD$species <- gsub("Diabrotica u. howardi", "Diabrotica undecimpunctata  howardi", SMD$species)
SMD$species <- gsub("Matrona basilaris japonica Fester", "Matrona japonica",SMD$species)

SMD$species <- as.factor(SMD$species)

#Repeat taxa creation after cleaning up the species name
taxa_smd <- tnrs_match_names(names = levels(SMD$species))

taxa_smd

#Make tree 
tree_smd <- tol_induced_subtree(ott_ids = taxa_smd[["ott_id"]], label_format = "name") 

#Plot tree to check
plot(tree_smd, cex=.8, label.offset =.1, no.margin = TRUE)

#See all tree labels
tree_smd$tip.label 

#Clean up the labels
tree_smd$tip.label <- gsub("_"," ", tree_smd$tip.label) #get rid of the underscores

#Check that there are no polytomies
is.binary(tree_smd)

set.seed(123)
tree_smd_binary <- ape::multi2di(tree_smd, random = TRUE)
is.binary(tree_smd_binary)

#Clean up the labels
tree_smd_binary$tip.label <- gsub("_"," ", tree_smd_binary$tip.label)

#Check for match between the labels in the tree and those in our species list
intersect(as.character(tree_smd_binary$tip.label), levels(SMD$species))

setdiff(levels(SMD$species), as.character(tree_smd_binary$tip.label))

setdiff(as.character(tree_smd_binary$tip.label), levels(SMD$species))

tree_smd_binary$tip.label <- gsub("Apis mellifera (species in domain Eukaryota)", "Apis mellifera", fixed=TRUE, tree_smd_binary$tip.label) #replace the tip label back with our species name
tree_smd_binary$tip.label <- gsub("Rhynchophorus ferrugineus (species in domain Eukaryota)", "Rhynchophorus ferrugineus", fixed=TRUE, tree_smd_binary$tip.label) #replace the tip label back with our species name

#Check that there are no polytomies again
is.binary(tree_smd_binary)

#saving SMD tree
#write.tree(tree_smd_binary, file = "tree_smd_binary.tre")
#tree_smd_binary <- read.tree(file = "tree_smd_binary.tre")
#Clean up the labels
#tree_smd_binary$tip.label <- gsub("_"," ", tree_smd_binary$tip.label)

tree_smd_binary <- compute.brlen(tree_smd_binary)
is.ultrametric(tree_smd_binary)

cor_tree_smd_binary <- vcv(tree_smd_binary,corr=T)

plot(tree_smd_binary)
```

```{r phylogeny SMD plot, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
SMD_taxa <- rotl::taxonomy_taxon_info(ott_id=taxa_smd$ott_id, include_lineage = TRUE)
str(tax_lineage(SMD_taxa))

#extract information on a few higher taxonomic levels in each species lineage
higher_taxa1 <- unlist(lapply(tax_lineage(SMD_taxa),function(x) x[5,3])) #class-level taxon names
higher_taxa2 <- unlist(lapply(tax_lineage(SMD_taxa),function(x) x[7,3])) #order-level1 taxon names
higher_taxa3 <- unlist(lapply(tax_lineage(SMD_taxa),function(x) x[9,3])) #order-level2 taxon names
higher_taxa4 <- unlist(lapply(tax_lineage(SMD_taxa),function(x) x[10,3])) #order-level3 taxon names

SMD_species_table <- tibble::tibble(species = taxa_smd$search_string, ott_id = taxa_smd$ott_id, higher1 = higher_taxa1, higher2 = higher_taxa2, higher3 = higher_taxa3, higher4 = higher_taxa4)

SMD_species_table <- SMD_species_table %>%
  dplyr::mutate(order = dplyr::case_when(
    higher1 %in% c("Acridomorpha", "Ensifera (suborder in Protostomia)", "Gryllidea", "Grylloidea", "Tettigoniidea") ~ "Orthoptera",
    higher1 %in% c("Apoidea", "Formicoidea") ~ "Hymenoptera",
    higher1 %in% c("Calyptratae", "Muscidae", "Drosophilini") ~ "Diptera",
    higher1 %in% c("Chrysomeloidea", "Cucujiformia", "Cucujoidea", "Staphyliniformia") ~ "Coleoptera",
    higher1 %in% c("Cicadidae", "Cimicomorpha") ~ "Hemiptera",
    higher1 %in% c("Danainae", "Obtectomera") ~ "Lepidoptera",
    higher1 %in% c("Entelegynae") ~ "Araneae",
    higher1 %in% c("Epiprocta", "Odonata") ~ "Odonata",
    higher1 %in% c("Termitoidae") ~ "Blattodea"
    ))

SMD_species_table$species <- stringr::str_to_sentence(SMD_species_table$species) 

SMD_species_table <- SMD_species_table %>% select(-c(ott_id, higher1, higher2,higher3, higher4))

SMD_species <- SMD %>%
	group_by(species) %>%
	summarise(count_ES = n(), count_K = n_distinct(paperid))

length(intersect(tree_smd_binary$tip.label, SMD_species$species))
length(intersect(SMD_species_table$species, SMD_species$species))

SMD_species <- merge(SMD_species, SMD_species_table, by = "species")

SMD_species$order <- as.factor(SMD_species$order)
SMD_species$species <- as.factor(SMD_species$species)

SMD_species_count_ES <- SMD_species$count_ES
names(SMD_species_count_ES) <- SMD_species$species #add row names
SMD_species_count_K <- SMD_species$count_K
names(SMD_species_count_K) <- SMD_species$species #add row names
SMD_species_order <- SMD_species$order
names(SMD_species_order) <- SMD_species$species #add row names

#ggtree
color_order_SMD <- c(Araneae="#009292", 
                     Blattodea="#FF6DB6", 
                     Coleoptera="#490092", 
                     Diptera="#006DDB", 
                     Hemiptera="#B66DFF", 
                     Hymenoptera="#6DB6FF", 
                     Lepidoptera="#920000", 
                     Odonata="#DB6D00", 
                     Orthoptera="#00d700")

smd_tree <- ggtree(tree_smd_binary, layout="fan", open.angle=15, ladderize = FALSE)

smd_tree <- rotate_tree(smd_tree, -90)

SMD_species_data <- as.data.frame(SMD_species)

smd_tree2 <- smd_tree %<+% SMD_species_data +
  geom_tiplab(aes(color=factor(order)),# color for label font
              show.legend = FALSE,
              align=TRUE,
              linetype=0,
              offset=0.05,
              size=4) +
  scale_color_manual(values=color_order_SMD)

smd_tree3 <-smd_tree2 +  
geom_fruit(geom=geom_bar,
           mapping=aes(y=label,x=count_K, fill=order),
           show.legend = FALSE,
           offset=1.5,
           pwidth=0.5,
           stat="identity",
           orientation="y",
           axis.params=list(
                         axis       = "x",
                         text.size  = 3.5,
                         hjust      = 1,
                         vjust      = 0.5,
                         nbreak     = 3,
                     ),
           grid.params=list()
         )+
         scale_fill_manual(values=color_order_SMD)

smd_tree4 <-smd_tree3 + new_scale_fill()+
geom_fruit(geom=geom_bar,
           mapping=aes(y=label,x=count_ES, fill=order),
           show.legend = FALSE,
           offset=0.1,
           pwidth=0.5,
           stat="identity",
           orientation="y",
            axis.params=list(
                         axis       = "x",
                         text.size  = 3.5,
                         hjust      = 1,
                         vjust      = 0.5,
                         nbreak     = 4,
                     ),
           grid.params=list()
         )+
         scale_fill_manual(values=color_order_SMD)

spider <- data.frame(node = c(41),
                            spider = c("bebd419e-f9d4-49c9-82bd-fa76c2449a06" #spider
                                         ))

termite <- data.frame(node = c(24),
                            termite = c("c248a577-d542-409f-9bdc-30fd61c6cce8" #termite
                                         ))

beetle <- data.frame(node = c(13),
                            beetle = c("986a7b1f-edbd-4751-bfee-427462552b5d"  #beetle
                                         ))

fly <- data.frame(node = c(7),
                            fly = c("31aba24a-a797-42bb-9601-5227d0dc8f75" #fly
                                         ))

cicada <- data.frame(node = c(22),
                            cicada = c("29af591e-9d31-4fef-8942-391367b542c5" #cicada
                                         ))

ant <- data.frame(node = c(19),
                            ant = c("592591ae-3b98-4129-8641-328ddb16580e" #ant
                                         ))

butterfly <- data.frame(node = c(2),
                            butterfly = c("0d4f6376-00fb-4056-afd7-dcb766573f2f" #butterfly
                                         ))

dragonfly <- data.frame(node = c(38),
                            dragonfly = c("36543d34-f5d6-48a1-818f-eca72bfe1a19" #dragonfly
                                         ))

cricket <- data.frame(node = c(27),
                            cricket = c("6e42ac62-37f4-458c-bf44-3f7decb1f14e" #cricket
                                         ))


smd_tree5 <- smd_tree4 %<+% spider + 
  geom_tiplab(aes(image=spider), geom="phylopic",offset=2.8, size=0.06, angle =0) 

smd_tree6 <- smd_tree5 %<+% termite + 
  geom_tiplab(aes(image=termite), geom="phylopic",offset=2.8, size=0.02, angle =0)

smd_tree7 <- smd_tree6 %<+% beetle + 
  geom_tiplab(aes(image=beetle), geom="phylopic",offset=2.8, size=0.03, angle =0)

smd_tree8 <- smd_tree7 %<+% fly + 
  geom_tiplab(aes(image=fly), geom="phylopic",offset=2.8, size=0.05, angle =0)

smd_tree9 <- smd_tree8 %<+% cicada + 
  geom_tiplab(aes(image=cicada), geom="phylopic",offset=2.8, size=0.03, angle =0)

smd_tree10 <- smd_tree9 %<+% ant + 
  geom_tiplab(aes(image=ant), geom="phylopic",offset=3.0, size=0.07, angle =0)

smd_tree11 <- smd_tree10 %<+% butterfly + 
  geom_tiplab(aes(image=butterfly), geom="phylopic",offset=2.8, size=0.06, angle =0)

smd_tree12 <- smd_tree11 %<+% dragonfly + 
  geom_tiplab(aes(image=dragonfly), geom="phylopic",offset=2.8, size=0.06, angle =0)

smd_tree13 <- smd_tree12 %<+% cricket + 
  geom_tiplab(aes(image=cricket), geom="phylopic",offset=2.8, size=0.03, angle =0)

smd_tree13
```

```{r phylogeny cor, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
#Run all
taxa_cor <- tnrs_match_names(names = levels(cor$species))
taxa_cor

#Clean species name 
cor$species <- gsub("Diabrotica u. howardi", "Diabrotica undecimpunctata  howardi", cor$species)
cor$species <- gsub("Matrona basilaris japonica Fester", "Matrona japonica",cor$species)
cor$species <- gsub("Canthon cyanelllus", "Canthon cyanellus",cor$species)
cor$species <- gsub("Gryllus veleti", "Gryllus veletis",cor$species)
cor$species <- gsub("Gryllus veletiss", "Gryllus veletis",cor$species)
cor$species <- gsub("Chrysophtharta agricola", "Paropsisterna agricola",cor$species)

cor$species <- as.factor(cor$species)

#Repeat taxa creation after cleaning up the species name
taxa_cor <- tnrs_match_names(names = levels(cor$species)) 

taxa_cor

#One species is not being classified in the tree for now. So we remove the data of the species. 
cor <- cor %>%
  filter(species != "Euoniticellus intermedius") %>%
  droplevels

cor$species <- as.factor(cor$species)

#Repeat taxa creation after cleaning up the species name
taxa_cor <- tnrs_match_names(names = levels(cor$species))

taxa_cor

#Make tree 
tree_cor <- tol_induced_subtree(ott_ids = taxa_cor[["ott_id"]], label_format = "name") 

#Plot tree to check
plot(tree_cor, cex=.8, label.offset =.1, no.margin = TRUE)

#See all tree labels
tree_cor$tip.label 

#Clean up the labels
tree_cor$tip.label <- gsub("_"," ", tree_cor$tip.label) #get rid of the underscores

#Check that there are no polytomies
is.binary(tree_cor)

set.seed(123)
tree_cor_binary <- ape::multi2di(tree_cor, random = TRUE)
is.binary(tree_cor_binary)

#Clean up the labels
tree_cor_binary$tip.label <- gsub("_"," ", tree_cor_binary$tip.label)

#Check for match between the labels in the tree and those in our species list
intersect(as.character(tree_cor_binary$tip.label), levels(cor$species))

setdiff(levels(cor$species), as.character(tree_cor_binary$tip.label))

setdiff(as.character(tree_cor_binary$tip.label), levels(cor$species))

tree_cor_binary$tip.label <- gsub("Bombus terrestris (species in domain Eukaryota)", "Bombus terrestris", fixed=TRUE, tree_cor_binary$tip.label) #replace the tip label back with our species name
tree_cor_binary$tip.label <- gsub("Diabrotica undecimpunctata howardi", "Diabrotica undecimpunctata  howardi", fixed=TRUE, tree_cor_binary$tip.label)
tree_cor_binary$tip.label <- gsub("Apis mellifera (species in domain Eukaryota)", "Apis mellifera", fixed=TRUE, tree_cor_binary$tip.label)

#Check that there are no polytomies again
is.binary(tree_cor_binary)

# saving cor tree
#write.tree(tree_cor_binary, file = "tree_cor_binary.tre")
#tree_cor_binary <- read.tree(file = "tree_cor_binary.tre")
#Clean up the labels
tree_cor_binary$tip.label <- gsub("_"," ", tree_cor_binary$tip.label)

tree_cor_binary <- compute.brlen(tree_cor_binary)
is.ultrametric(tree_cor_binary)

cor_tree_cor_binary <- vcv(tree_cor_binary,corr=T)

plot(tree_cor_binary)
```

```{r phylogeny cor plot, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
cor_taxa <- rotl::taxonomy_taxon_info(ott_id=taxa_cor$ott_id, include_lineage = TRUE)
str(tax_lineage(cor_taxa))

#extract information on a few higher taxonomic levels in each species lineage
higher_taxa1 <- unlist(lapply(tax_lineage(cor_taxa),function(x) x[5,3])) #class-level taxon names
higher_taxa2 <- unlist(lapply(tax_lineage(cor_taxa),function(x) x[7,3])) #order-level1 taxon names
higher_taxa3 <- unlist(lapply(tax_lineage(cor_taxa),function(x) x[9,3])) #order-level2 taxon names
higher_taxa4 <- unlist(lapply(tax_lineage(cor_taxa),function(x) x[10,3])) #order-level3 taxon names

cor_species_table <- tibble::tibble(species = taxa_cor$search_string, ott_id = taxa_cor$ott_id, higher1 = higher_taxa1, higher2 = higher_taxa2, higher3 = higher_taxa3, higher4 = higher_taxa4)

table(cor_species_table$higher1)

cor_species_table <- cor_species_table %>%
  dplyr::mutate(order = dplyr::case_when(
    higher1 %in% c("Acridomorpha", "Ensifera (suborder in Protostomia)", "Gryllidea", "Grylloidea", "Tettigoniidea") ~ "Orthoptera",
    higher1 %in% c("Anthozoa") ~ "Actiniaria",
    higher1 %in% c("Apidae", "Apoidea", "Formicoidea", "Vespoidea") ~ "Hymenoptera",
    higher1 %in% c("Arachnida") ~ "Pseudoscorpiones",
    higher1 %in% c("Araneae", "Entelegynae") ~ "Araneae",
    higher1 %in% c("Carabidae", "Chrysomeloidea", "Cucujiformia", "Cucujoidea", "Luperini", "Polyphaga (suborder in cohort Holometabola)", "Scarabaeiformia", "Scarabaeoidea", "Staphyliniformia") ~ "Coleoptera",
    higher1 %in% c("Dacinae", "Drosophilinae", "Drosophilini", "Tephritidae") ~ "Diptera",
    higher1 %in% c("Epiprocta", "Odonata") ~ "Odonata",
    higher1 %in% c("Forficulina") ~ "Dermaptera",
    higher1 %in% c("Gammarida", "Peracarida") ~ "Amphipoda",
    higher1 %in% c("Neoptera") ~ "Mecoptera",
    higher1 %in% c("Nymphalidae", "Obtectomera") ~ "Lepidoptera",
    higher1 %in% c("Thoracotremata") ~ "Decapoda",
    higher1 %in% c("Vetigastropoda") ~ "Lepetellida"
    ))

cor_species_table$species <- stringr::str_to_sentence(cor_species_table$species) 

cor_species_table <- cor_species_table %>% select(-c(ott_id, higher1, higher2,higher3, higher4))

cor_species <- cor %>%
	group_by(species) %>%
	summarise(count_ES = n(), count_K = n_distinct(paperid))

length(intersect(tree_cor_binary$tip.label, cor_species$species))
length(intersect(cor_species_table$species, cor_species$species))

cor_species <- merge(cor_species, cor_species_table, by = "species")

cor_species$order <- as.factor(cor_species$order)
cor_species$species <- as.factor(cor_species$species)

cor_species_count_ES <- cor_species$count_ES
names(cor_species_count_ES) <- cor_species$species #add row names
cor_species_count_K <- cor_species$count_K
names(cor_species_count_K) <- cor_species$species #add row names
cor_species_order <- cor_species$order
names(cor_species_order) <- cor_species$species #add row names

#ggtree
color_order_cor <- c(Actiniaria="#000000",
                     Amphipoda="#004949",
                     Araneae="#009292", 
                     Coleoptera="#490092", 
                     Decapoda="#FF6DB6", 
                     Dermaptera="#FFB6DB", 
                     Diptera="#006DDB", 
                     Hymenoptera="#6DB6FF", 
                     Lepetellida="#B66DFF", 
                     Lepidoptera="#920000", 
                     Mecoptera="#924900", 
                     Odonata="#DB6D00", 
                     Orthoptera="#00d700", 
                     Pseudoscorpiones="#FFB900")

cor_tree <- ggtree(tree_cor_binary, layout="fan", open.angle=15, ladderize = FALSE)

cor_tree <- rotate_tree(cor_tree, -90)

cor_species_data <- as.data.frame(cor_species)

cor_species_data$species2 <- cor_species_data$species

cor_species_data$species2 <- gsub("Diabrotica undecimpunctata  howardi", "Diabrotica u. howardi",  cor_species_data$species2)

cor_species_data <- as.data.frame(cor_species_data)

cor_tree2 <- cor_tree %<+% cor_species_data +
  geom_tiplab(aes(label=species2, color=factor(order)),# color for label font
              show.legend = FALSE,
              align=TRUE,
              linetype=0,
              offset=0.05,
              size=4) +
  scale_color_manual(values=color_order_cor)

cor_tree3 <-cor_tree2 +  
geom_fruit(geom=geom_bar,
           mapping=aes(y=label,x=count_K, fill=order),
           show.legend = FALSE,
           offset=1.5,
           pwidth=0.5,
           stat="identity",
           orientation="y",
           axis.params=list(
                         axis       = "x",
                         text.size  = 3.5,
                         hjust      = 1,
                         vjust      = 0.5,
                         nbreak     = 3,
                     ),
           grid.params=list()
         )+
         scale_fill_manual(values=color_order_cor)

cor_tree4 <-cor_tree3 + new_scale_fill()+
geom_fruit(geom=geom_bar,
           mapping=aes(y=label,x=count_ES, fill=order),
           show.legend = FALSE,
           offset=0.1,
           pwidth=0.5,
           stat="identity",
           orientation="y",
            axis.params=list(
                         axis       = "x",
                         text.size  = 3.5,
                         hjust      = 1,
                         vjust      = 0.5,
                         nbreak     = 4,
                     ),
           grid.params=list()
         )+
         scale_fill_manual(values=color_order_cor)

coral <- data.frame(node = c(72),coral = c("19cbe092-a0f1-4107-b6f3-2dffeeda2668"))
amphipod <- data.frame(node = c(66),amphipod = c("9440c5d0-123e-4aac-930e-d2d5f8b0b63e"))
spider <- data.frame(node = c(69),spider = c("bebd419e-f9d4-49c9-82bd-fa76c2449a06"))
beetle <- data.frame(node = c(13),beetle = c("986a7b1f-edbd-4751-bfee-427462552b5d"))
crab <- data.frame(node = c(67),crab = c("4c918335-ace1-4986-ab04-316ba42685b0"))
earwig <- data.frame(node = c(27),earwig = c("3fd92960-bac6-4cd4-bcf6-584c27ee2758"))
fly <- data.frame(node = c(4),fly = c("31aba24a-a797-42bb-9601-5227d0dc8f75"))
bee <- data.frame(node = c(24),bee = c("5dbec3ce-247b-48cd-9556-ddbc9ce5eef7"))
abalone <- data.frame(node = c(1),abalone = c("fbac183c-ec4b-474a-8f0a-15e2154d6b39"))
butterfly <- data.frame(node = c(2),butterfly = c("0d4f6376-00fb-4056-afd7-dcb766573f2f"))
scorpionfly <- data.frame(node = c(7),scorpionfly = c("54865c84-198f-41c0-b125-7e599b757d6c"))
dragonfly <- data.frame(node = c(57),dragonfly = c("36543d34-f5d6-48a1-818f-eca72bfe1a19"))
cricket <- data.frame(node = c(32),cricket = c("6e42ac62-37f4-458c-bf44-3f7decb1f14e"))
pseudoscorpion <- data.frame(node = c(71), pseudoscorpion = c("59d4edd3-75a8-45cc-8749-ca8ecaeeee8e"))


cor_tree5 <- cor_tree4 %<+% coral + 
  geom_tiplab(aes(image=coral), geom="phylopic",offset=2.8, size=0.04, angle =0) 

cor_tree6 <- cor_tree5 %<+% amphipod + 
  geom_tiplab(aes(image=amphipod), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree7 <- cor_tree6 %<+% spider + 
  geom_tiplab(aes(image=spider), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree8 <- cor_tree7 %<+% beetle + 
  geom_tiplab(aes(image=beetle), geom="phylopic",offset=2.8, size=0.03, angle =0)

cor_tree9 <- cor_tree8 %<+% crab + 
  geom_tiplab(aes(image=crab), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree10 <- cor_tree9 %<+% earwig + 
  geom_tiplab(aes(image=earwig), geom="phylopic",offset=2.8, size=0.06, angle =0)

cor_tree11 <- cor_tree10 %<+% fly + 
  geom_tiplab(aes(image=fly), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree12 <- cor_tree11 %<+% bee + 
  geom_tiplab(aes(image=bee), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree13 <- cor_tree12 %<+% abalone + 
  geom_tiplab(aes(image=abalone), geom="phylopic",offset=2.7, size=0.03, angle =0)

cor_tree14 <- cor_tree13 %<+% butterfly + 
  geom_tiplab(aes(image=butterfly), geom="phylopic",offset=2.9, size=0.05, angle =0)

cor_tree15 <- cor_tree14 %<+% scorpionfly + 
  geom_tiplab(aes(image=scorpionfly), geom="phylopic",offset=2.8, size=0.06, angle =0)

cor_tree16 <- cor_tree15 %<+% dragonfly + 
  geom_tiplab(aes(image=dragonfly), geom="phylopic",offset=2.8, size=0.05, angle =0)

cor_tree17 <- cor_tree16 %<+% cricket + 
  geom_tiplab(aes(image=cricket), geom="phylopic",offset=2.8, size=0.03, angle =0)

cor_tree18 <- cor_tree17 %<+% pseudoscorpion + 
  geom_tiplab(aes(image=pseudoscorpion), geom="phylopic",offset=2.8, size=0.045, angle =0)

cor_tree18

```

```{r SMD dataset, echo = FALSE, results = "hide", messages = FALSE}
#Cleaning up the dataset
SMD <- SMD[complete.cases(SMD$yi),]

##Create the effect size id, the sample id, and the phylogeny id for the random effects first
SMD$phylogeny <- SMD$species

SMD_imm_manip <- SMD %>% filter(immunity_or_reproduction=="immunity") 

SMD_repro_manip <- SMD %>% filter(immunity_or_reproduction=="reproduction")
```

```{r calculatek, echo = FALSE, results = "hide", messages = FALSE}
#Counting k numbers 
paper_n_smd <- n_distinct(SMD$paperid)
es_n_smd <- n_distinct(SMD$esid)
species_n_smd <- n_distinct(SMD$species)

paper_n_smd_imm <- n_distinct(SMD_imm_manip$paperid)
es_n_smd_imm <- n_distinct(SMD_imm_manip$esid)
species_n_smd_imm <- n_distinct(SMD_imm_manip$species)

paper_n_smd_repro <- n_distinct(SMD_repro_manip$paperid)
es_n_smd_repro <- n_distinct(SMD_repro_manip$esid)
species_n_smd_repro <- n_distinct(SMD_repro_manip$species)

paper_n_cor <- n_distinct(cor$paperid)
es_n_cor <- n_distinct(cor$esid)
species_n_cor <- n_distinct(cor$species)

#Count the total number of species in total
species_SMD <- SMD %>% select(species)
species_cor <- cor %>% select(species)

species_total <- rbind(species_cor,species_SMD)

species_n_total <- n_distinct(species_total$species)

#Count the total number of papers in total
paper_SMD <- SMD %>% select(paperid)
paper_cor <- cor %>% select(paperid)

paper_total <- rbind(paper_cor,paper_SMD)

paper_n_total <- n_distinct(paper_total$paperid)


```

```{r figtreesmd, warning=FALSE, fig.cap="Phylogenetic trees for (A) experimental studies and (B) correlational studies, along with the number of studies (inner ring) and effect sizes (outer ring) on each species.", echo = FALSE, fig.height = 26, fig.width = 13, dpi=300, fig.align = "center"}

plot_trees <- cor_tree18 +
  smd_tree13 + 
    plot_layout(widths = c(1, 1),
                heights = c(1, 1),
              design = "
              1
              2
              ") + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 25))

plot_trees
```

# Correlational studies

```{r cor random effects, echo = FALSE, results = "hide", messages = FALSE}
cor$vi_zr <- (cor$se_zr)^2

#Create the effect size id, the sample id, and the phylogeny id for the random effects first
cor$phylogeny <- cor$species

#Deciding on random effects structure
res1REML_cor <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|species, ~1|paperid,~1|studyid,~1|experiment,~1|esid),
                        method="REML",data = cor, R= list(phylogeny = cor_tree_cor_binary),sparse=T,
                       test="t",
                        control=list(optimizer="BFGS"))

i2_cor <- i2_ml(res1REML_cor)

#Minor contribution from study and experimental identity. Test if they improve the goodness of fit on top of the major contributors to i2 heterogeneity
res2REML_cor_wostudyexp <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        method="REML",
                       data = cor, 
                       R= list(phylogeny = cor_tree_cor_binary),
                       sparse=T,
                       test="t",
                        control=list(optimizer="BFGS"))

res2REML_cor_wstudyexp <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|paperid,~1|studyid,~1|experiment,~1|esid),
                        method="REML",
                       data = cor, 
                       R= list(phylogeny = cor_tree_cor_binary),
                       sparse=T,
                       test="t",
                        control=list(optimizer="BFGS"))

AICc(res2REML_cor_wostudyexp,res2REML_cor_wstudyexp)

#Including the 2 actually worsens AICc. Just keep to the 3 major ones. 
```

### Overall effect

```{r overall r, echo = FALSE, results = "hide", messages = FALSE}
res2REML_cor <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        method="REML",
                       data = cor, 
                       R= list(phylogeny = cor_tree_cor_binary),
                       sparse=T,
                       test="t",
                        control=list(optimizer="BFGS"))

summary(res2REML_cor)

res2REML_cor_RVE <- robust(res2REML_cor, cluster = cor$paperid)

res2REML_cor_RVE

```

```{r coroverall, warning=FALSE, fig.cap="Orchard plot for overall correlation betweeen reproductive investment and immune function. The circles represent individual effect sizes. Size of each circle represents the sample size for that effect size. The thin line represents the 95% prediction interval. The rectangle represents the 95% confidence interval. The dot in the middle represents the average effect size.", fig.height = 4, fig.width = 4, dpi=300,out.width="50%",fig.align = "center", echo=FALSE}

orchard_plot(res2REML_cor_RVE, 
             xlab=expression("Pearson's"~italic(r)),
             angle = 45, 
             group = "paperid", 
             transfm = "tanh",
             trunk.size = 3, 
             branch.size = 2.5, 
             twig.size = 0.5) +
  scale_fill_viridis_d(begin = 0.3, option="C")+
  scale_colour_viridis_d(begin = 0.3, option="C")+
  scale_x_discrete(labels = c("Intrcpt"=""))


```

## Moderator analysis 

### Checking moderators first

```{r mod check cor, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
cor<- cor %>% mutate(parasite_vs_immune = if_else(immune_response_type == "other",as.character(immune_response_other),as.character(immune_response_type))) 

cor$parasite_vs_immune <- as.factor(cor$parasite_vs_immune)

table(cor$parasite_vs_immune)

cor$parasite_vs_immune <- recode(cor$parasite_vs_immune,
                                 "Antimicrobial activity" = "immune",
                                 "bacterial load" = "parasite",
                     "cuticular melanization" = "immune",
                     "encapsulation"="immune",
                     "haemocytes"="immune",
                     "hydrolitic enzyme"="immune",
                     "longevity post-infection"="immune",
                     "lytic"="immune",
                     "Lytic"="immune",
                     "Nitric oxide assay"="immune",
                     "parasite load"="parasite",
                     "parasite presence"="parasite",
                     "parasite resistance"="parasite",
                     "percentage phagocytosis" ="immune",
                     "phagocytic index"="immune",
         "PO"="immune",
         "survival"="immune",
         "total hemocyte count"="immune",
         "total phagocytic capacity"="immune")

cor_mods <- cor %>% select(precopulatory_postcopulatory_traits,
                           constitutive_induced,
                           pre_or_post_species,
                           female_mating_frequency,
                           contest_scramble,
                           order,
                           parasite_vs_immune)

table(cor$precopulatory_postcopulatory_traits)
table(cor$constitutive_induced)
table(cor$pre_or_post_species)
table(cor$female_mating_frequency)
table(cor$contest_scramble)
table(cor$order)
table(cor$parasite_vs_immune)

##use Goodman and Kruskal’s τ measure of association between categorical predictor variables (function from package GoodmanKruskal: 
GKmatrix_cor <- GKtauDataframe(cor_mods)
plot(GKmatrix_cor)

cor$female_mating_frequency1<-recode(cor$female_mating_frequency,
                     "high" = "high",
                     "low"="low/monogamous",
                     "monogamous"="low/monogamous")
```

## Main moderator analysis

```{r cor main moderator, echo = FALSE, results = "hide", messages = FALSE}
eval(metafor:::.MuMIn)

keepVars_cor <- c("yi_zr", 
              "vi_zr",
              "phylogeny",
              "species",
              "paperid",
              "esid",
              "precopulatory_postcopulatory_traits",
              "constitutive_induced",
              "female_mating_frequency1",
              "contest_scramble",
              "parasite_vs_immune")

cor_compl <- cor[, keepVars_cor] #dataset with these variables only

cor_compl <- cor_compl[complete.cases(cor_compl),] #removes missing values, two ocean species, one coral and one shellfish were removed because they don't belong to either contest or scramble

#Trimming tree for just the ones included in the model selection
myspecies_cor_compl <- as.character(unique(cor_compl$species))
length(myspecies_cor_compl) 
setdiff(tree_cor_binary$tip.label, myspecies_cor_compl) 
tree_cor_binary_compl <- keep.tip(tree_cor_binary, myspecies_cor_compl) 
tree_cor_binary_compl <- compute.brlen(tree_cor_binary_compl)
is.ultrametric(tree_cor_binary_compl)
cor_tree_cor_binary_compl <- vcv(tree_cor_binary_compl,corr=T)

cor_compl$phylogeny <- cor_compl$species

res_cor_modsel <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ relevel(factor(precopulatory_postcopulatory_traits),ref="postcopulatory") +
                          factor(constitutive_induced) +
                          factor(female_mating_frequency1) +
                          factor(contest_scramble) +
                          factor(parasite_vs_immune), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_modsel)

cor_candidate.models <- dredge(res_cor_modsel)

cor_subset.models<- subset(cor_candidate.models, delta < 2)
model.sel(cor_subset.models)

#Null model is second best model. We will take null as the most parsimonious explanation. But let's run the model averaging to see the averaged effects. 

#Average models with RVE

mod_cor2 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(constitutive_induced), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_cor1 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ 1, 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))


mod_cor3 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(contest_scramble), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))



mod_cor4 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(constitutive_induced) +
                          factor(contest_scramble), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))


mod_cor6 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(constitutive_induced) +
                          factor(female_mating_frequency1), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_cor5 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid, ~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(female_mating_frequency1), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_cor10 <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_compl),
                        mods = ~ factor(constitutive_induced) +
                          factor(parasite_vs_immune), 
                        method="ML",
                        data = cor_compl, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))


mod_cor2_RVE <- robust(mod_cor2, cluster = cor_compl$paperid)
mod_cor1_RVE <- robust(mod_cor1, cluster = cor_compl$paperid)
mod_cor3_RVE <- robust(mod_cor3, cluster = cor_compl$paperid)
mod_cor4_RVE <- robust(mod_cor4, cluster = cor_compl$paperid)
mod_cor6_RVE <- robust(mod_cor6, cluster = cor_compl$paperid)
mod_cor5_RVE <- robust(mod_cor5, cluster = cor_compl$paperid)
mod_cor10_RVE <- robust(mod_cor10, cluster = cor_compl$paperid)

modsel_cor_RVE<- model.sel(mod_cor2_RVE,
                   mod_cor1_RVE,
                   mod_cor3_RVE,
                   mod_cor4_RVE,
                   mod_cor6_RVE,
                   mod_cor5_RVE,
                   mod_cor10_RVE,
                   rank = "AICc")

avg_cor_RVE <- model.avg(modsel_cor_RVE)

summary(avg_cor_RVE)
confint(avg_cor_RVE)
```

```{r corfigmod, warning=FALSE, fig.cap="Orchard plot of moderator effects for correlational studies by (A) immune measure, (B) immune vs parasite measures, (C) investment type, (D) female mating frequency, and (E) male competition type. In each plot, the circles represent individual effect sizes. Size of each circle represents the sample size for that effect size. The thin lines represent the 95% prediction interval. The rectangles represent the 95% confidence interval. The dots in the middle represent the average effect size.", fig.height = 8, fig.width = 8, dpi=300,fig.align = "center", echo=FALSE}

res_cor_prepost <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(precopulatory_postcopulatory_traits), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_prepost_RVE <- robust(res_cor_prepost, cluster = cor$paperid)

prepost_traits_cor <- orchard_plot(res_cor_prepost_RVE,
             mod = "precopulatory_postcopulatory_traits",
             xlab=expression("Pearson's"~italic(r)),
             group = "paperid",
             transfm = "tanh",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_x_discrete(labels = c("Precopulatory"="Pre-mating", "Postcopulatory" = "Post-mating"))

res_cor_coninduc <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(constitutive_induced), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_coninduc_RVE <- robust(res_cor_coninduc, cluster = cor$paperid)

coninduc_cor <- orchard_plot(res_cor_coninduc_RVE,
             mod = "constitutive_induced",
             xlab=expression("Pearson's"~italic(r)),
             group = "paperid",
             transfm = "tanh",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_cor_polyandry <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(female_mating_frequency1), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_polyandry_RVE <- robust(res_cor_polyandry, cluster = cor$paperid)

polyandry_cor <- orchard_plot(res_cor_polyandry_RVE,
             mod = "female_mating_frequency1",
             xlab=expression("Pearson's"~italic(r)),
             group = "paperid",
             transfm = "tanh",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_cor_contscram <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(contest_scramble), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_contscram_RVE <- robust(res_cor_contscram, cluster = cor$paperid)

contscram_cor <- orchard_plot(res_cor_contscram_RVE,
             mod = "contest_scramble",
             xlab=expression("Pearson's"~italic(r)),
             transfm = "tanh",
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_cor_parimm <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(parasite_vs_immune), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_parimm_RVE <- robust(res_cor_parimm, cluster = cor$paperid)

parimm_cor <- orchard_plot(res_cor_parimm_RVE,
             mod = "parasite_vs_immune",
             xlab=expression("Pearson's"~italic(r)),
             transfm = "tanh",
             group = "paperid",
             angle = 45)+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

coninduc_cor+
  parimm_cor+
  prepost_traits_cor+ 
  polyandry_cor + 
  contscram_cor + 
  guide_area() +  plot_annotation(tag_levels = 'A') + 
    plot_layout(widths = c(1, 1),
                guides ="collect",
              design = "
              12
              34
              56")
```

```{r corparamest, tab.cap="Model parameter estimates for correlational studies that tested the correlation between immune function and reproductive traits.", echo = FALSE, messages = FALSE, warning=FALSE}

res2REML_cor_paramest <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        method="REML",data = cor, R= list(phylogeny = cor_tree_cor_binary),sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res2REML_cor_paramest_RVE <- as.data.frame(coef(summary(robust(res2REML_cor_paramest, cluster = cor$paperid))))

res_cor_prepost_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(precopulatory_postcopulatory_traits)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_prepost_paramest_RVE <- as.data.frame(coef(summary(robust(res_cor_prepost_paramest, cluster = cor$paperid))))

res_cor_coninduc_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(constitutive_induced)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_coninduc_paramest_RVE <- as.data.frame(coef(summary(robust(res_cor_coninduc_paramest, cluster = cor$paperid))))

res_cor_polyandry_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(female_mating_frequency1)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_polyandry_paramest_RVE <- as.data.frame(coef(summary(robust(res_cor_polyandry_paramest, cluster = cor$paperid))))

res_cor_contscram_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(contest_scramble)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_contscram_paramest_RVE <- as.data.frame(coef(summary(robust(res_cor_contscram_paramest, cluster = cor$paperid))))

res_cor_parimm_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(parasite_vs_immune)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_cor_parimm_paramest_RVE <- as.data.frame(coef(summary(robust(res_cor_parimm_paramest, cluster = cor$paperid))))

param_cor <- rbind(res2REML_cor_paramest_RVE,
                          res_cor_prepost_paramest_RVE,
                          res_cor_coninduc_paramest_RVE,
                          res_cor_polyandry_paramest_RVE,
                          res_cor_contscram_paramest_RVE,
                          res_cor_parimm_paramest_RVE) 

rows <- c(1, 4, 6, 8,10)

for (i in rev(rows)) {
  param_cor <- tibble::add_row(param_cor, .after =i)
}

param_cor$term <- c("Overall",
                           "Investment type",
                           "Both",
                           "Postcopulatory",
                           "Precopulatory",
                           "Immune measure",
                           "Constitutive",
                           "Induced",
                           "Female mating frequency",
                           "High",
                           "Monogamous/Low",
                           "Male competition type",
                           "Contest",
                           "Scramble",
                           "Immune vs Parasite measure",
                           "Immune",
                           "Parasite load")

param_cor <- param_cor[, c(8, 1, 2, 3,4,5,6,7)]

param_cor[2:8] <- lapply(param_cor[2:8], as.numeric)

param_cor <- param_cor %>%
    mutate(pval = case_when(pval < 0.001 ~ '< 0.001',
                            pval >= 0.001 ~ format(round(as.numeric(pval),3),nsmall=3)),
           estimate = metafor::transf.ztor(estimate),
           ci.lb = metafor::transf.ztor(ci.lb),
           ci.ub = metafor::transf.ztor(ci.ub))

ft_param_cor <- flextable(param_cor) %>% 
  set_header_labels(values = list(
    term = "",
    estimate = "Pearson's r",
    "se" = "se",
    "tval" = "t value",
    "df" = "df",
    "pval" ="p value",
    "ci.lb" ="95% CI lower",
    "ci.ub" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(align = "center", part = "header") %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "right") %>% 
  flextable::align(i = c(1,2,6,9,12,15),j = 1, align = "left") %>% 
  flextable::delete_columns(j = c('se', 'tval', 'df'))%>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_param_cor
```

## Additional analysis - Linnean order

```{r cor moderator order, echo = FALSE, results = "hide", messages = FALSE}
#Testing Linnean order instead of female mating frequency and male competition type

#Let's first have a look the distribution of effect sizes across orders
table(cor$order)

#Looks like a few orders with very small sample sizes. Looking at the tree, the following orders also have only one paper on each of them: Decapoda, Dermaptera, Lepetellida, Lepidoptera, Mecoptera, Pseudoscorpiones, Scleractinia. Note that any significant effects involving these should be taken cautiously.

#Compute effct size across orders using univariate models first

res_cor_order_paramest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(order)-1, 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

#Unable to run robust because using paperid as clustering variable because multiple orders with just one paper. Proceed with just non-robust estimates.
summary(res_cor_order_paramest)

#Diptera with the largest (and positive) effect size and Lepetellida with that smallest (and negative).

#Comparing Diptera with the rest of the orders. Note. No other comparisons were significant. 
res_cor_order <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ relevel(factor(order),ref="Diptera"), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_order)

#Transforming zr to r
res_cor_order <- as.data.frame(coef(summary(res_cor_order)))

res_cor_order <- res_cor_order %>%
    mutate(estimate = metafor::transf.ztor(estimate),
           ci.lb = metafor::transf.ztor(ci.lb),
           ci.ub = metafor::transf.ztor(ci.ub))

```

```{r cororder, warning=FALSE, fig.cap="Orchard plot of moderator effects for correlational studies by Linnean order. In each plot, the circles represent individual effect sizes. Size of each circle represents the sample size for that effect size. The thin lines represent the 95% prediction interval. The rectangles represent the 95% confidence interval. The dots in the middle represent the average effect size.", fig.height = 10, fig.width = 5, dpi=300,fig.align = "center", echo=FALSE}

res_cor_order <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ factor(order), 
                        method="REML",
                        data = cor, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

order_cor <- orchard_plot(res_cor_order,
             mod = "order",
             xlab=expression("Pearson's"~italic(r)),
             group = "paperid",
             transfm = "tanh",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

order_cor

```

```{r orderparamest, tab.cap="Model parameter estimates for correlational studies by Linnean order.", echo = FALSE, messages = FALSE, warning=FALSE}


res_cor_order_paramest <- as.data.frame(coef(summary(res_cor_order_paramest)))


res_cor_order_paramest$term <- c("Amphipoda",
                           "Araneae",
                           "Coleoptera",
                           "Decapoda",
                           "Dermaptera",
                           "Diptera",
                           "Hymenoptera",
                           "Lepetellida",
                           "Lepidoptera",
                           "Mecoptera",
                           "Odonata",
                           "Orthoptera",
                           "Pseudoscorpiones",
                           "Scleractinia")

res_cor_order_paramest <- res_cor_order_paramest[, c(8, 1, 2, 3,4,5,6,7)]

res_cor_order_paramest[2:8] <- lapply(res_cor_order_paramest[2:8], as.numeric)

res_cor_order_paramest <- res_cor_order_paramest %>%
    mutate(pval = case_when(pval < 0.001 ~ '< 0.001',
                            pval >= 0.001 ~ format(round(as.numeric(pval),3),nsmall=3)),
           estimate = metafor::transf.ztor(estimate),
           ci.lb = metafor::transf.ztor(ci.lb),
           ci.ub = metafor::transf.ztor(ci.ub))

ft_order_cor <- flextable(res_cor_order_paramest) %>% 
  set_header_labels(values = list(
    term = "",
    estimate = "Pearson's r",
    "se" = "se",
    "tval" = "tval",
    "df" = "df",
    "pval" ="p value",
    "ci.lb" ="95% CI lower",
    "ci.ub" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(align = "center", part = "header") %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "right") %>% 
  flextable::delete_columns(j = c('se', 'tval', 'df'))%>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_order_cor 


```

## Targeted analysis - mixers vs non-mixers

```{r mixers subset cor, echo = FALSE, results = "hide", messages = FALSE}
cor_postcop <- cor %>% filter(precopulatory_postcopulatory_traits=="postcopulatory") 

cor_ejac <- cor_postcop %>%  filter(SS_assayed!="mating effort") %>% 
  filter(SS_assayed!="nuptial gift") %>% 
  filter(SS_assayed!="attractiveness/unclear modality") %>% 
  filter(SS_assayed!="other") %>% 
  filter(SS_assayed!="mating success") 
table(cor_ejac$precedence)

cor_ejac$precedence1<-recode(cor_ejac$precedence,
                     "mixing" = "mixing",
                     "precedence_first"="precedence",
                     "precedence_last"="precedence")

#Trimming tree for just the species included in this analysis
myspecies_cor_ejac <- as.character(unique(cor_ejac$species))
length(myspecies_cor_ejac) 
setdiff(tree_cor_binary$tip.label, myspecies_cor_ejac) 
tree_cor_binary_ejac <- keep.tip(tree_cor_binary, myspecies_cor_ejac) 
tree_cor_binary_ejac <- compute.brlen(tree_cor_binary_ejac)
is.ultrametric(tree_cor_binary_ejac)
cor_tree_cor_binary_ejac <- vcv(tree_cor_binary_ejac,corr=T)

cor_ejac$phylogeny <- cor_ejac$species

#Moderator model
res_cor_ejac <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_ejac),
                        mods = ~ factor(precedence1), 
                        method="REML",
                        data = cor_ejac, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_ejac)

res_cor_ejac_RVE <- robust(res_cor_ejac,cluster=cor_ejac$paperid)

summary(res_cor_ejac_RVE)

#Average effect size estimation
res_cor_ejac_nointercept <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_ejac),
                        mods = ~ factor(precedence1)-1, 
                        method="REML",
                        data = cor_ejac, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_ejac_nointercept)

res_cor_ejac_nointercept_RVE <- robust(res_cor_ejac_nointercept,cluster=cor_ejac$paperid)

summary(res_cor_ejac_nointercept_RVE)

res_cor_ejac_nointercept_RVE <- as.data.frame(coef(summary(res_cor_ejac_nointercept_RVE)))

res_cor_ejac_nointercept_RVE <- res_cor_ejac_nointercept_RVE %>%
    mutate(estimate = metafor::transf.ztor(estimate),
           ci.lb = metafor::transf.ztor(ci.lb),
           ci.ub = metafor::transf.ztor(ci.ub))
```

## Targeted analysis - trait type for contest competitors

```{r contest subset cor, echo = FALSE, results = "hide", messages = FALSE}
cor_contest <- cor %>% filter(contest_scramble=="contest") 

table(cor_contest$SS_assayed)

cor_contest$SS_assayed1<-recode(cor_contest$SS_assayed,
                                "acoustic"="auditory",
                     "sperm competitiveness"="ejaculate traits")

cor_contest <- cor_contest %>% filter(SS_assayed1!="ejaculate traits") %>% 
  filter(SS_assayed1!="other") %>% 
  filter(SS_assayed1!="nuptial gift") %>% 
  filter(SS_assayed1!="mating success")%>% 
  filter(SS_assayed1!="attractiveness/unclear modality") %>% 
  filter(SS_assayed1!="mating effort")%>% 
  filter(SS_assayed1!="mating success")%>% 
  filter(SS_assayed1!="reproductive ouput")%>% 
  filter(SS_assayed1!="reproductive output")

table(cor_contest$SS_assayed1)

#Trimming tree
myspecies_cor_contest <- as.character(unique(cor_contest$species))
length(myspecies_cor_contest) 
setdiff(tree_cor_binary$tip.label, myspecies_cor_contest) 
tree_cor_binary_contest <- keep.tip(tree_cor_binary, myspecies_cor_contest) 
tree_cor_binary_contest <- compute.brlen(tree_cor_binary_contest)
is.ultrametric(tree_cor_binary_contest)
cor_tree_cor_binary_contest <- vcv(tree_cor_binary_contest,corr=T)

cor_contest$phylogeny <- cor_contest$species

#Moderator model
res_cor_contest <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_contest),
                        mods = ~ relevel(factor(SS_assayed1),ref ="dominance"), 
                        method="REML",
                        data = cor_contest, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_contest)

#Average effect estimation
res_cor_contest_no_intercept <- rma.mv(yi=yi_zr, V=vi_zr, 
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary_contest),
                        mods = ~ factor(SS_assayed1)-1, 
                        method="REML",
                        data = cor_contest, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_cor_contest_no_intercept)

res_cor_contest_no_intercept <- as.data.frame(coef(summary(res_cor_contest_no_intercept)))

res_cor_contest_no_intercept <- res_cor_contest_no_intercept %>%
    mutate(estimate = metafor::transf.ztor(estimate),
           ci.lb = metafor::transf.ztor(ci.lb),
           ci.ub = metafor::transf.ztor(ci.ub))


```

# Experimental studies

```{r i2 SMD, echo = FALSE, results = "hide", messages = FALSE}

#Deciding on random effects structure. Run model with all possible random effects.
res1REML_mean <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|phylogeny,
                                     ~1|species, 
                                     ~1|paperid,
                                     ~1|studyid,
                                     ~1|experiment,
                                     ~1|esid),
                        method="REML",
                        data = SMD, 
                        R= list(phylogeny = cor_tree_smd_binary),
                        sparse=T, 
                        test = "t",
                        control=list(optimizer="BFGS")
                        )

#Looking at i2 contributed by each random effect
i2_SMD <- i2_ml(res1REML_mean)
```

```{r overall SMD, echo = FALSE, results = "hide", messages = FALSE}

res2REML_mean <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        method="REML",
                        data = SMD, 
                        sparse=T, 
                        test = "t",
                        control=list(optimizer="BFGS"))

summary(res2REML_mean)

res2REML_mean_RVE <- robust(res2REML_mean, cluster = paperid)

res2REML_mean_RVE

transf.dtorbis(res2REML_mean_RVE$b[1,])
transf.dtorbis(res2REML_mean_RVE$ci.lb[1])
transf.dtorbis(res2REML_mean_RVE$ci.ub[1])

res2REML_mean_design <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mod=~ factor(immunity_or_reproduction),
                        method="REML",
                        data = SMD, 
                        sparse=T, 
                        test = "t",
                        control=list(optimizer="BFGS"))

summary(res2REML_mean_design)

res2REML_mean_design_RVE <- robust(res2REML_mean_design, cluster = SMD$paperid)

res2REML_mean_design_RVE

res2REML_mean_design_nointercept <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mod=~ factor(immunity_or_reproduction)-1,
                        method="REML",
                        data = SMD, 
                        sparse=T, 
                        test = "t",
                        control=list(optimizer="BFGS"))

summary(res2REML_mean_design_nointercept)

transf.dtorbis(res2REML_mean_design_nointercept$b[1,])
transf.dtorbis(res2REML_mean_design_nointercept$ci.lb[1])
transf.dtorbis(res2REML_mean_design_nointercept$ci.ub[1])

transf.dtorbis(res2REML_mean_design_nointercept$b[2,])
transf.dtorbis(res2REML_mean_design_nointercept$ci.lb[2])
transf.dtorbis(res2REML_mean_design_nointercept$ci.ub[2])


```

```{r figsmdoverall, warning=FALSE, fig.cap="Orchard plots of the (A) overall results and (B) results split by experimental design for experiments testing the effect of reproductive investment on immune function and vice versa. The black rectangles represent the 95% confidence intervals, and the dot within represents the mean effect size. The thin lines represent the 95% prediction intervals. In each plot, the circles represent individual effect sizes, with the size of each circle reflecting the sample size.", echo = FALSE, fig.height = 7, fig.width = 13,dpi=300, fig.align = "center"}

overall <- orchard_plot(res2REML_mean_RVE, 
                        xlab=expression("Hedges'"~italic(D)),
                        angle = 45, 
                        group = "paperid", 
                        trunk.size = 3, 
                        branch.size = 2.5, 
                        twig.size = 0.5) +
  theme(text=element_text(size=15),
        axis.text.y = element_text(size=15),
        axis.text.x = element_text(size=15),
        legend.title = element_text(size =12)) +
  scale_fill_viridis_d(begin = 0.3, option="C")+
  scale_colour_viridis_d(begin = 0.3, option="C")+
  scale_x_discrete(labels = c("Intrcpt"=""))

design <- orchard_plot(res2REML_mean_design_RVE,
             mod = "immunity_or_reproduction",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             trunk.size = 3, 
             branch.size = 2.5, 
             twig.size = 0.5)+
  theme(text=element_text(size=15),
        axis.text.y = element_text(size=15),
        axis.text.x = element_text(size=15),
        legend.title = element_text(size =12))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_x_discrete(labels = c("Reproduction"="Sexual trait \nexpression", "Immunity" = "Immunity"))

overall + design +  plot_annotation(tag_levels = 'A') 
```

## Moderator analysis

#### Moderator checks

```{r mod check immune, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
#Looking at immune manipulation studies first

table(SMD_imm_manip$experimental_immune_elicitor)
table(SMD_imm_manip$precopulatory_postcopulatory_traits)
table(SMD_imm_manip$developmental_stage)
table(SMD_imm_manip$pre_or_post_species)
table(SMD_imm_manip$female_mating_frequency)
table(SMD_imm_manip$contest_scramble)
table(SMD_imm_manip$order)

SMD_imm_manip$ecto_endo<-recode(SMD_imm_manip$experimental_immune_elicitor,
                     "ectoparasite" = "ecto",
                     "endoparasite"="endo",
                     "fungus"="endo",
                     "heat-killed fungus"="endo",
                     "heat-killed bacteria"="endo",
                     "live bacteria"="endo",
                     "LPS"="endo",
                     "nonlive_endoparasite"="endo",
                     "other"="endo")

SMD_imm_manip$live_nonlive<-recode(SMD_imm_manip$pathogenlive,
                     "1" = "live",
                     "0"="nonlive")

SMD_imm_manip$female_mating_frequency2<-recode(SMD_imm_manip$female_mating_frequency,
                     "high" = "high",
                     "low"="low/monogamous",
                     "monogamous"="low/monogamous")

table(SMD_imm_manip$ecto_endo)
table(SMD_imm_manip$live_nonlive)
table(SMD_imm_manip$female_mating_frequency2)

SMD_imm_manip_mods <- SMD_imm_manip %>% select(ecto_endo,
                                              live_nonlive,
                                               precopulatory_postcopulatory_traits,
                                               developmental_stage,
                                               pre_or_post_species,
                                               female_mating_frequency2,
                                               contest_scramble,
                                               order)

##use Goodman and Kruskal’s τ measure of association between categorical predictor variables (function from package GoodmanKruskal: 
GKmatrix_imm_manip <- GKtauDataframe(SMD_imm_manip_mods)
plot(GKmatrix_imm_manip)

#Looking at the results, there is high association between order and a number of the other moderators. Therefore, we will remove order first. We also remove pre/post species because it is quite strongly related to female mating frequency.

#Moderators to keep for the immune manipulation studies
#ecto_endo,
#live_nonlive
#precopulatory_postcopulatory_traits
#developmental_stage
#female_mating_frequency2
#contest_scramble

#Running the same for reproduction manipulation studies

table(SMD_repro_manip$precopulatory_postcopulatory_traits) #remove
table(SMD_repro_manip$constitutive_induced)
table(SMD_repro_manip$pre_or_post_species) #remove
table(SMD_repro_manip$female_mating_frequency)
table(SMD_repro_manip$contest_scramble)
table(SMD_repro_manip$order)

SMD_repro_manip$female_mating_frequency2<-recode(SMD_repro_manip$female_mating_frequency,
                     "high" = "high",
                     "low"="low/monogamous",
                     "monogamous"="low/monogamous")

SMD_repro_manip_mods <- SMD_repro_manip %>% select(constitutive_induced,
                                                   female_mating_frequency2,
                                                   contest_scramble,
                                                   order)

##Run the categorical association analysis on all pairwise data 
GKmatrix_repro_manip <- GKtauDataframe(SMD_repro_manip_mods)
plot(GKmatrix_repro_manip)

#Remove order

#Moderators to keep for the reproduction manipulation studies
#constitutive_induced
#female_mating_frequency2
#contest_scramble
```

### Main moderator analysis 

```{r SMD main moderator, echo = FALSE, results = "hide", messages = FALSE}
#Model selection
eval(metafor:::.MuMIn)

keepVars <- c("yi", 
              "vi",
              "paperid",
              "esid",
              "ecto_endo",
                "live_nonlive",
                "precopulatory_postcopulatory_traits",
                "developmental_stage",
                "female_mating_frequency2",
                "contest_scramble")

SMD_imm_manip_compl <- SMD_imm_manip[, keepVars] #dataset with these variables only

SMD_imm_manip_compl <- SMD_imm_manip_compl[complete.cases(SMD_imm_manip_compl),] #removes missing values


res_mean_imm_manip_modsel <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          relevel(factor(precopulatory_postcopulatory_traits),ref="precopulatory") +
                          factor(developmental_stage) +
                          factor(female_mating_frequency2) +
                          factor(contest_scramble),
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_modsel_RVE <- robust(res_mean_imm_manip_modsel, cluster = paperid)

summary(res_mean_imm_manip_modsel_RVE)

imm_manip_candidate.models <- dredge(res_mean_imm_manip_modsel)

imm_manip_subset.models<- subset(imm_manip_candidate.models, delta < 2)
model.sel(imm_manip_subset.models)

#Average models with RVE

mod_imm_manip23 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(developmental_stage),
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))

mod_imm_manip55 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
               mods = ~ relevel(factor(precopulatory_postcopulatory_traits),ref="precopulatory") +
                 factor(developmental_stage) + 
                 factor(live_nonlive)+
                 factor(ecto_endo),
               method="ML",
               data = SMD_imm_manip_compl,
               sparse=T,
               test="t",
                        control=list(optimizer="BFGS"))

mod_imm_manip24 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(developmental_stage) +
                          factor(contest_scramble),
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))

mod_imm_manip23_RVE <- robust(mod_imm_manip23, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip55_RVE <- robust(mod_imm_manip55, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip24_RVE <- robust(mod_imm_manip24, cluster = SMD_imm_manip_compl$paperid)

modsel_imm_manip_RVE<- model.sel(mod_imm_manip23_RVE,
                   mod_imm_manip24_RVE,
                   mod_imm_manip55_RVE,
                   rank = "AICc")

avg_imm_manip_RVE <- model.avg(modsel_imm_manip_RVE)

summary(avg_imm_manip_RVE)
confint(avg_imm_manip_RVE)

#For reproduction manipulation studies
keepVars_repro <- c("yi", 
              "vi",
              "paperid",
              "esid",
              "female_mating_frequency2",
                "contest_scramble",
                "constitutive_induced")

SMD_repro_manip_compl <- SMD_repro_manip[, keepVars_repro] #dataset with these variables only

SMD_repro_manip_compl <- SMD_repro_manip_compl[complete.cases(SMD_repro_manip_compl),] #removes missing values

res_mean_repro_manip_modsel <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2) +
                          factor(contest_scramble)+
                          factor(constitutive_induced),
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

repro_manip_candidate.models <- dredge(res_mean_repro_manip_modsel)

repro_manip_subset.models<- subset(repro_manip_candidate.models, delta < 2)
model.sel(repro_manip_subset.models)
# The null model is one of the models that were within 2 AICc points from the best model. We go with the null.

#But let's run the model averaging to see what the results look like 

#Average models with RVE

mod_repro_manip2 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(constitutive_induced),
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip1 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~1,
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip5 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2),
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip6 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2) +
                          factor(constitutive_induced),
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip2_RVE <- robust(mod_repro_manip2, cluster = SMD_repro_manip_compl$paperid)
mod_repro_manip1_RVE <- robust(mod_repro_manip1, cluster = SMD_repro_manip_compl$paperid)
mod_repro_manip5_RVE <- robust(mod_repro_manip5, cluster = SMD_repro_manip_compl$paperid)
mod_repro_manip6_RVE <- robust(mod_repro_manip6, cluster = SMD_repro_manip_compl$paperid)

modsel_repro_manip_RVE<- model.sel(mod_repro_manip2_RVE,
                   mod_repro_manip1_RVE,
                   mod_repro_manip5_RVE,
                   mod_repro_manip6_RVE,
                   rank = "AICc")

avg_repro_manip_RVE <- model.avg(modsel_repro_manip_RVE)

summary(avg_repro_manip_RVE)
confint(avg_repro_manip_RVE)
```

```{r figimmmod, warning=FALSE, fig.cap="Orchard plot of moderator effects for immune challenge experiments by (A) parasite type, (B) challenge type, (C) investment type, (D) female mating frequency, (E) male competition type, and (F) developmental stage at which the immune challenge occurred. In each plot, the circles represent individual effect sizes. Size of each circle represents the sample size for that effect size. The thin lines represent the 95% prediction interval. The rectangles represent the 95% confidence interval. The dots in the middle represent the average effect size.", fig.height = 15, fig.width = 10, dpi=300,fig.align = "center", echo=FALSE}

res_mean_imm_manip_end_ect <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_end_ect_RVE <- robust(res_mean_imm_manip_end_ect, cluster = SMD_imm_manip$paperid)

end_ect_imm <- orchard_plot(res_mean_imm_manip_end_ect_RVE,
             mod = "ecto_endo",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_mean_imm_manip_live_nonlive <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(live_nonlive), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_live_nonlive_RVE <- robust(res_mean_imm_manip_live_nonlive, cluster = SMD_imm_manip$paperid)

live_nonlive_imm <- orchard_plot(res_mean_imm_manip_live_nonlive_RVE,
             mod = "live_nonlive",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_mean_imm_prepost <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(precopulatory_postcopulatory_traits), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_prepost_RVE <- robust(res_mean_imm_prepost, cluster = SMD_imm_manip$paperid)

prepost_traits_imm <- orchard_plot(res_mean_imm_prepost_RVE,
             mod = "precopulatory_postcopulatory_traits",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_x_discrete(labels = c("Precopulatory"="Pre-mating", "Postcopulatory" = "Post-mating"))

res_mean_imm_devstg <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(developmental_stage), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_devstg_RVE <- robust(res_mean_imm_devstg, cluster = SMD_imm_manip$paperid)

devstg_imm <- orchard_plot(res_mean_imm_devstg_RVE,
             mod = "developmental_stage",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_mean_imm_polyandry <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_polyandry_RVE <- robust(res_mean_imm_polyandry, cluster = SMD_imm_manip$paperid)

polyandry_imm <- orchard_plot(res_mean_imm_polyandry_RVE,
             mod = "female_mating_frequency2",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_mean_imm_contscram <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(contest_scramble), 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_contscram_RVE <- robust(res_mean_imm_contscram, cluster = SMD_imm_manip$paperid)

contscram_imm <- orchard_plot(res_mean_imm_contscram_RVE,
             mod = "contest_scramble",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("bottom.left"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

plot_imm <- end_ect_imm + 
  live_nonlive_imm + 
  prepost_traits_imm + 
  polyandry_imm + 
  contscram_imm + 
  devstg_imm + 
  guide_area() +  plot_annotation(tag_levels = 'A') + 
    plot_layout(widths = c(1, 1),
                guides ="collect",
              design = "
              12
              34
              56
              78
              ") &
  theme(axis.title.x = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text =element_text(size = 15),
        legend.title =element_text(size = 15))

plot_imm
```

```{r immmanipparamest, tab.cap="Model parameter estimates for experiments that tested the effects of an immune challenge on reproductive investment.", echo = FALSE, messages = FALSE, warning = FALSE}
res_mean_imm_manip_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_manip_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_manip_end_ect_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_end_ect_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_manip_end_ect_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_manip_live_nonlive_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(live_nonlive)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_live_nonlive_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_manip_live_nonlive_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_prepost_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(precopulatory_postcopulatory_traits)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_prepost_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_prepost_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_devstg_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(developmental_stage)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_devstg_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_devstg_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_polyandry_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_polyandry_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_polyandry_paramest, cluster = SMD_imm_manip$paperid))))

res_mean_imm_contscram_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(contest_scramble)-1, 
                        method="REML",
                        data = SMD_imm_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_imm_contscram_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_imm_contscram_paramest, cluster = SMD_imm_manip$paperid))))

param_mean <- rbind(res_mean_imm_manip_paramest_RVE,
                    res_mean_imm_manip_end_ect_paramest_RVE,
                    res_mean_imm_manip_live_nonlive_paramest_RVE,
                    res_mean_imm_prepost_paramest_RVE, 
                    res_mean_imm_devstg_paramest_RVE, 
                    res_mean_imm_polyandry_paramest_RVE,
                    res_mean_imm_contscram_paramest_RVE) 

rows <- c(1, 3, 5, 8, 10,12)

for (i in rev(rows)) {
  param_mean <- tibble::add_row(param_mean, .after =i)
}

param_mean$term <- c("Overall",
                  "Parasite type",
                  "Ectoparasite",
                  "Endoparasite",
                  "Challenge",
                  "Live",
                  "Non-live",
                  "Investment type",
                  "Both",
                  "Postcopulatory",
                  "Precopulatory",
                  "Developmental stage",
                  "Adult",
                  "Juvenile",
                  "Female mating frequency",
                  "High",
                  "Monogamous/Low",
                  "Male competition type",
                  "Contest",
                  "Scramble")

param_mean <- param_mean[, c(8, 1, 2, 3,4,5,6,7)]

param_mean[2:8] <- lapply(param_mean[2:8], as.numeric)

param_mean <- param_mean %>%
    mutate(pval = case_when(pval < 0.001 ~ '< 0.001',
                            pval >= 0.001 ~ format(round(as.numeric(pval),3),nsmall=3)))

ft_param_mean <- flextable(param_mean) %>% 
  set_header_labels(values = list(
    term = "",
    estimate = "Hedges' D",
    "se" = "se",
    "tval" = "t value",
    "df" = "df",
    "pval" ="p value",
    "ci.lb" ="95% CI lower",
    "ci.ub" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(align = "center", part = "header") %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "right") %>% 
  flextable::align(i = c(1,2,5,8,12,15,18),j = 1, align = "left") %>% 
  flextable::delete_columns(j = c('se', 'tval', 'df')) %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_param_mean
```

```{r figrepromod, warning=FALSE, fig.cap="Orchard plot of moderator effects for reproductive investment manipulation studies by (A) female mating frequency, (B) male competition type, and (C) immune outcome type. In each plot, the circles represent individual effect sizes. Size of each circle represents the sample size for that effect size. The thin lines represent the 95% prediction interval. The rectangles represent the 95% confidence interval. The dots in the middle represent the average effect size.", fig.height = 7, fig.width = 7, dpi=300,fig.align = "center", echo=FALSE}

res_mean_repro_polyandry <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2), 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_polyandry_RVE <- robust(res_mean_repro_polyandry, cluster = SMD_repro_manip$paperid)

polyandry_repro <- orchard_plot(res_mean_repro_polyandry_RVE,
             mod = "female_mating_frequency2",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none")) +
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

res_mean_repro_contscram <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(contest_scramble), 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_contscram_RVE <- robust(res_mean_repro_contscram, cluster = SMD_repro_manip$paperid)

contscram_repro <- orchard_plot(res_mean_repro_contscram_RVE,
             mod = "contest_scramble",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45,
             legend.pos= c("none"))+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")


res_mean_repro_coninduc <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(constitutive_induced), 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_coninduc_RVE <- robust(res_mean_repro_coninduc, cluster = SMD_repro_manip$paperid)

coninduc_repro <- orchard_plot(res_mean_repro_coninduc_RVE,
             mod = "constitutive_induced",
             xlab=expression("Hedges'"~italic(D)),
             group = "paperid",
             angle = 45)+
  scale_fill_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")+
  scale_colour_viridis_d(begin = 0.3, end = 0.8, direction = -1, option="C")

plot_repro<- polyandry_repro + contscram_repro+ coninduc_repro + guide_area() +  plot_annotation(tag_levels = 'A') + 
    plot_layout(widths = c(1, 1),
                guides ="collect",
              design = "
              12
              34
              ") &
  theme(axis.title.x = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.text =element_text(size = 12),
        legend.title =element_text(size = 12))

plot_repro
```

```{r repromanipparamest, tab.cap="Model parameter estimates for experiments that tested the effect of reproductive investment in immune function.", echo = FALSE, messages = FALSE, warning=FALSE}

res_mean_repro_manip_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_manip_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_repro_manip_paramest, cluster = SMD_repro_manip$paperid))))

res_mean_repro_polyandry_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2)-1, 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_polyandry_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_repro_polyandry_paramest, cluster = SMD_repro_manip$paperid))))

res_mean_repro_contscram_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(contest_scramble)-1, 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_contscram_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_repro_contscram_paramest, cluster = SMD_repro_manip$paperid))))

res_mean_repro_coninduc_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(constitutive_induced)-1, 
                        method="REML",
                        data = SMD_repro_manip, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

res_mean_repro_coninduc_paramest_RVE <- as.data.frame(coef(summary(robust(res_mean_repro_coninduc_paramest, cluster = SMD_repro_manip$paperid))))

param_mean_repro <- rbind(res_mean_repro_manip_paramest_RVE,
                          res_mean_repro_polyandry_paramest_RVE,
                          res_mean_repro_contscram_paramest_RVE,
                          res_mean_repro_coninduc_paramest_RVE) 

rows <- c(1, 3, 5)

for (i in rev(rows)) {
  param_mean_repro <- tibble::add_row(param_mean_repro, .after =i)
}

param_mean_repro$term <- c("Overall",
                  "Female mating frequency",
                  "High",
                  "Monogamous/Low",
                  "Male competition type",
                  "Contest",
                  "Scramble",
                  "Immune outcome",
                  "Constitutive",
                  "Induced")

param_mean_repro <- param_mean_repro[, c(8, 1, 2, 3,4,5,6,7)]

param_mean_repro[2:8] <- lapply(param_mean_repro[2:8], as.numeric)

param_mean_repro <- param_mean_repro %>%
    mutate(pval = case_when(pval < 0.001 ~ '< 0.001',
                            pval >= 0.001 ~ format(round(as.numeric(pval),3),nsmall=3)))

ft_param_mean_repro <- flextable(param_mean_repro) %>% 
  set_header_labels(values = list(
    term = "",
    estimate = "Hedges' d",
    "se" = "se",
    "tval" = "t value",
    "df" = "df",
    "pval" ="p value",
    "ci.lb" ="95% CI lower",
    "ci.ub" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(align = "center", part = "header") %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "right") %>% 
  flextable::align(i = c(1,2,5,8),j = 1, align = "left") %>% 
  flextable::delete_columns(j = c('se', 'tval', 'df'))%>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_param_mean_repro
```

### Targeted analysis - mixers vs non-mixers

```{r mixers subset, echo = FALSE, results = "hide", messages = FALSE}
#Subset analysis
SMD_postcop <- SMD %>% filter(precopulatory_postcopulatory_traits=="postcopulatory") 

SMD_ejac <- SMD_postcop %>%  filter(SS_assayed!="nuptial gift") %>% 
  filter(SS_assayed!="chemical") 
table(SMD_ejac$SS_assayed)
table(SMD_ejac$precedence)

SMD_ejac$precedence1<-recode(SMD_ejac$precedence,
                     "displacement" = "nonmixing",
                     "mixing"="mixing",
                     "precedence_last"="nonmixing")

#Note analysis had to exclude 1 data point which looked at ejaculate traits in an monogamous species Musca
res_mean_ejac <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ relevel(factor(precedence1), ref = "mixing"), 
                        method="REML",
                        data = SMD_ejac, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_mean_ejac)

res_mean_ejac_RVE <- robust(res_mean_ejac, cluster = SMD_ejac$paperid)

res_mean_ejac_RVE

res_mean_ejac_paramest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ relevel(factor(precedence1), ref = "mixing")-1, 
                        method="REML",
                        data = SMD_ejac, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_mean_ejac_paramest)

res_mean_ejac_paramest_RVE <- robust(res_mean_ejac_paramest, cluster = SMD_ejac$paperid)

res_mean_ejac_paramest_RVE
```

### Targeted analysis - trait type for contest competitiors

```{r contest subset, echo = FALSE, results = "hide", messages = FALSE}
SMD_contest <- SMD %>% filter(contest_scramble=="contest") 

table(SMD_contest$SS_assayed)

SMD_contest$SS_assayed1<-recode(SMD_contest$SS_assayed,
                                "acoustic" = "auditory",
                     "ejaculate"="ejaculate traits",
                     "sperm competitiveness"="ejaculate traits",
                     "reproductive ouput"="reproductive output")

SMD_contest <- SMD_contest %>% filter(SS_assayed1!="ejaculate traits") %>% 
  filter(SS_assayed1!="other") %>% 
  filter(SS_assayed1!="nuptial gift") %>% 
  filter(SS_assayed1!="mating success") %>% 
  filter(SS_assayed1!="reproductive output")%>% 
  filter(SS_assayed1!="attractiveness/unclear modality")%>% 
  filter(SS_assayed1!="mating effort")%>% 
  filter(SS_assayed1!="weapon")

table(SMD_contest$SS_assayed1)

res_mean_contest <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ relevel(factor(SS_assayed1),ref="dominance"), 
                        method="REML",
                        data = SMD_contest, 
                        sparse=T,
                        test="t")

summary(res_mean_contest)

res_mean_contest_RVE <- robust(res_mean_contest, cluster = paperid)

summary(res_mean_contest_RVE)

res_mean_contest_no_intercept <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(SS_assayed1)-1, 
                        method="REML",
                        data = SMD_contest, 
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

summary(res_mean_contest_no_intercept)

res_mean_contest_no_intercept_RVE <- robust(res_mean_contest_no_intercept, cluster = paperid)

summary(res_mean_contest_no_intercept_RVE)
```

# Publication bias

```{r Pub bias smd, echo = FALSE, results = "hide", messages = FALSE}
SMD_imm_manip$inv_n_tilda <-  with(SMD_imm_manip, (n_control + n_experimental)/(n_control*n_experimental))
SMD_imm_manip$sqrt_inv_n_tilda <-  with(SMD_imm_manip, sqrt(inv_n_tilda))
SMD_imm_manip$centered_year <- with(SMD_imm_manip, scale(year_published,scale=FALSE))

pub_bias_imm_manip <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(precopulatory_postcopulatory_traits) +
                          factor(developmental_stage) +
                          factor(contest_scramble)+
                          sqrt_inv_n_tilda+
                          centered_year, 
                        method="REML",
                        test="t", 
                        data = SMD_imm_manip, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

pub_bias_imm_manip_RVE <- robust(pub_bias_imm_manip, cluster=SMD_imm_manip$paperid)

summary(pub_bias_imm_manip_RVE)

SMD_repro_manip$inv_n_tilda <-  with(SMD_repro_manip, (n_control + n_experimental)/(n_control*n_experimental))
SMD_repro_manip$sqrt_inv_n_tilda <-  with(SMD_repro_manip, sqrt(inv_n_tilda))
SMD_repro_manip$centered_year <- with(SMD_repro_manip, scale(year_published,scale=FALSE))

pub_bias_repro_manip <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ sqrt_inv_n_tilda+
                          centered_year, 
                        method="REML",
                        test="t", 
                        data = SMD_repro_manip, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

pub_bias_repro_manip_RVE <- robust(pub_bias_repro_manip, cluster=SMD_repro_manip$paperid)

summary(pub_bias_repro_manip_RVE)
```

```{r Pub bias cor, echo = FALSE, results = "hide", messages = FALSE}
cor$inv_n_tilda <-  with(cor, 1/(n_correlation))
cor$sqrt_inv_n_tilda <-  with(cor, sqrt(inv_n_tilda))
cor$centered_year <- with(cor, scale(year_published,scale=FALSE))

pub_bias_cor <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ sqrt_inv_n_tilda+
                          centered_year, 
                        method="REML",
                        test="t", 
                        data = cor, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

pub_bias_cor_RVE <- robust(pub_bias_cor, cluster=cor$paperid)

summary(pub_bias_cor_RVE)
```

```{r Pub bias smd fig prep, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
res_mean_imm_manip <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(precopulatory_postcopulatory_traits) +
                          factor(developmental_stage) +
                          factor(contest_scramble), 
                        method="REML",
                        test="t", 
                        data = SMD_imm_manip, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

funnel(res_mean_imm_manip,yaxis="vinv")

funnel_imm <- recordPlot()

yearREML_imm_fig <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ year_published, 
                        method="REML",
                        data = SMD_imm_manip,
                        sparse = T,
                        test="t",
                        control=list(optimizer="BFGS"))

yearREML_imm_fig <- robust(yearREML_imm_fig, cluster = SMD_imm_manip$paperid)

year_imm_fig <- bubble_plot(yearREML_imm_fig, mod = "year_published", 
            xlab = "Publication year", ylab = expression("Hedges'"~italic(D)),
            group = "paperid", legend.pos = "none")+ theme(plot.margin = unit(c(1,1,1,1), "cm"))

res_mean_repro_manip <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        method="REML",
                        test="t", 
                        data = SMD_repro_manip, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

funnel(res_mean_repro_manip,yaxis="vinv", xlab =expression("Hedges'"~italic(D)))

funnel_repro<- recordPlot()

yearREML_repro_fig <- rma.mv(yi=yi, V=vi,  
                        random= list(~1|paperid,~1|esid),
                        mods = ~ year_published, 
                        method="REML",
                        data = SMD_repro_manip,
                        sparse = T,
                        test="t",
                        control=list(optimizer="BFGS"))

yearREML_repro_fig_RVE <- robust(yearREML_repro_fig, cluster = SMD_repro_manip$paperid)

year_repro_fig <- bubble_plot(yearREML_repro_fig_RVE, mod = "year_published", 
            xlab = "Publication year", ylab = expression("Hedges'"~italic(D)),
            group = "paperid",legend.pos = "none")+ theme(plot.margin = unit(c(1,1,1,1), "cm"))
```

```{r smdpubbias, warning=FALSE, fig.cap="Publication bias results for experimental studies: (A) funnel plot of effect size residuals after controlling for the moderators that were retained by our AICc model selection, plotted against the standard error for immune manipulation studies, (B) relationship between year of publication and effect size for immune manipulation studies, (C) funnel plot for reproductive trait manipulation studies (no moderators were included since the null model was regarded as the most parsimonious from our AICc model selection), (D) relationship between year of publication and effect size for reproductive trait manipulation studies.", echo = FALSE, fig.height = 10, fig.width = 10, dpi=300,fig.align = "center"}


plot1<- plot_grid(funnel_imm,                                  
          year_imm_fig, 
          ncol = 2,
          nrow = 1,
          hjust = - 1.5,
          labels = c('A', 'B'))

plot2 <- plot_grid(funnel_repro,
          year_repro_fig,
          ncol = 2,
          nrow = 1,
          hjust = - 1.5,
          labels = c('C', 'D'))

plot_combined <- plot_grid(plot1,
                           NULL,
          plot2,
          ncol = 1,
          nrow = 3,
          rel_heights = c(2,0.4,2))
plot_combined
```

```{r Pub bias cor fig prep, echo = FALSE, results = "hide", messages = FALSE, fig.show='hide'}
res_mean_cor <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny,~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        method="REML",
                        test="t", 
                        data = cor, 
                        sparse=T,
                        control=list(optimizer="BFGS"))

funnel(res_mean_cor,yaxis="vinv", xlab =expression(italic(Zr)))

funnel_cor <- recordPlot()

yearREML_cor_fig <- rma.mv(yi=yi_zr, V=vi_zr,  
                        random= list(~1|phylogeny, ~1|paperid,~1|esid),
                        R= list(phylogeny = cor_tree_cor_binary),
                        mods = ~ year_published, 
                        method="REML",
                        data = cor,
                        sparse = T,
                        test="t",
                        control=list(optimizer="BFGS"))

yearREML_cor_fig_RVE <- robust(yearREML_cor_fig, cluster = cor$paperid)

year_cor_fig <- bubble_plot(yearREML_cor_fig_RVE, mod = "year_published", 
            xlab = "Publication year", ylab = expression(italic(Zr)),
            group = "paperid",legend.pos = "none")

```

```{r corpubbias, warning=FALSE, fig.cap="Publication bias results for correlational studies: (A) funnel plot of effect size plotted against standard error, (B) relationship between year of publication and effect size.", echo = FALSE, fig.height = 5, fig.width = 10,dpi=300, fig.align = "center"}
plot_grid(funnel_cor,                                  
          year_cor_fig, 
          ncol = 2,
          hjust = - 1.5,
          labels = c('A', 'B'))
```

# Supplementary material

## Supplementary tables

```{r i2manip, tab.cap="I2 heterogeneity accounted for by each random effect for experimental studies", echo = FALSE}
#Check i2 of the random effects 
i2_SMD <- as.data.frame(i2_ml(res1REML_mean))

rownames(i2_SMD) <- c("Total","Phylogeny","Species id","Paper id","Study id","Experiment id","Effect size id")

ft_SMD <- flextable(i2_SMD%>% rownames_to_column("Random effect"))

ft_SMD <- set_header_labels(ft_SMD,
    "i2_ml(res1REML_mean)" = "I2 (%)"
  ) %>%
  colformat_double(digits = 2) %>%
  align(align = "center", part = "all")%>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_SMD
```

```{r i2cor, tab.cap="I2 heterogeneity accounted for by each random effect for correlational studies", echo=FALSE}
#Check i2 of the random effects 
i2_cor<- as.data.frame(i2_ml(res1REML_cor))

rownames(i2_cor) <- c("Total","Phylogeny","Species id","Paper id","Study id","Experiment id","Effect size id")

ft_cor <- flextable(i2_cor%>% rownames_to_column("Random effect"))

ft_cor <- set_header_labels(ft_cor,
    "i2_ml(res1REML_cor)" = "I2 (%)"
  ) %>%
  colformat_double(digits = 2) %>%
align(align = "center", part = "all")%>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_cor
``` 

```{r immmanipmodels, tab.cap="AICc model selection table for experiments that tested the effect of an immune challenge on reproductive investment. Models presented are those that were within 2 AICc points from the best fit model.", echo = FALSE, messages = FALSE, warning = FALSE}
imm_manip_selectmod <- as.data.frame(model.sel(imm_manip_subset.models))

ft_imm_manip_selectmod <- flextable(imm_manip_selectmod) %>% 
  set_header_labels(values = list(
    "(Intercept)" = "Intercept",
    "factor(contest_scramble)" ="Male competition type",
    "factor(developmental_stage)" ="Developmental stage",
    "factor(ecto_endo)" ="Parasite type",
    "factor(live_nonlive)" ="Challenge type",
    'relevel(factor(precopulatory_postcopulatory_traits), ref = "precopulatory")' ="Investment type")) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_imm_manip_selectmod 
```

```{r immmanipselect, tab.cap="Averaged model results from AICc model selection for experiments that tested the effects of an immune challenge on reproductive investment.", echo = FALSE, messages = FALSE, warning = FALSE}
avg_imm_manip_res<-as.data.frame(summary(avg_imm_manip_RVE)$coefmat.subset)
avg_imm_manip_CI<-as.data.frame(confint(avg_imm_manip_RVE))

avg_imm_manip <- cbind(avg_imm_manip_res,
                           avg_imm_manip_CI)

avg_imm_manip$term <- c("Intercept",
                  "Parasite type: Endoparasite",
                  "Challenge type: Non-live",
                  "Developmental stage: Juvenile",
                  "Investment type: Pre- and Post-",
                  "Investment type: Post-mating",
                  "Male competition type: Scramble")

avg_imm_manip <- avg_imm_manip[, c(7, 1, 2, 3,4,5,6)]

avg_imm_manip[2:7] <- lapply(avg_imm_manip[2:7], as.numeric)

ft_avg_imm_manip <- flextable(avg_imm_manip) %>% 
  set_header_labels(values = list(
    term = "",
    "df" = "df",
    "Pr(>|z|)" ="p value",
    "2.5 %" ="95% CI lower",
    "97.5 %" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_avg_imm_manip
```

```{r repromanipmodels, tab.cap="AICc model selection table for experiments that tested the effect of reproductive investment on immune function. Models presented are those that were within 2 AICc points from the best fit model.", echo = FALSE, messages = FALSE, warning = FALSE}
repro_manip_selectmod <- as.data.frame(model.sel(repro_manip_subset.models))

ft_repro_manip_selectmod <- flextable(repro_manip_selectmod) %>% 
  set_header_labels(values = list(
    "(Intercept)" = "Intercept",
    "factor(constitutive_induced)" = "Immune outcome",
    "factor(female_mating_frequency2)" ="Female mating frequency")) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_repro_manip_selectmod
```

```{r repromanipselect, tab.cap="Averaged model results from AICc model selection for experiments that tested the effects of reproductive investment on immune function.", echo = FALSE, messages = FALSE, warning = FALSE}
avg_repro_manip_res<-as.data.frame(summary(avg_repro_manip_RVE)$coefmat.subset)
avg_repro_manip_CI<-as.data.frame(confint(avg_repro_manip_RVE))

avg_repro_manip <- cbind(avg_repro_manip_res,
                           avg_repro_manip_CI)

avg_repro_manip$term <- c("Intercept",
                  "Immune outcome: Induced",
                  "Female mating frequency: Low/monogamous")

avg_repro_manip <- avg_repro_manip[, c(7, 1, 2, 3,4,5,6)]

avg_repro_manip[2:7] <- lapply(avg_repro_manip[2:7], as.numeric)

ft_avg_repro_manip <- flextable(avg_repro_manip) %>% 
  set_header_labels(values = list(
    term = "",
    "df" = "df",
    "Pr(>|z|)" ="p value",
    "2.5 %" ="95% CI lower",
    "97.5 %" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_avg_repro_manip
```

```{r cormodels, tab.cap="AICc model selection table for correlational studies on the relationship between reproductive investment and immune function. Models presented are those that were within 2 AICc points from the best fit model.", echo = FALSE, messages = FALSE, warning = FALSE}
cor_selectmod <- as.data.frame(model.sel(cor_subset.models))

ft_cor_selectmod <- flextable(cor_selectmod) %>% 
  set_header_labels(values = list(
    "(Intercept)" = "Intercept",
    "factor(constitutive_induced)" = "Immune outcome",
    "factor(contest_scramble)" ="Male competitive type",
    "factor(female_mating_frequency1)" ="Female mating frequency",
    "factor(parasite_vs_immune)" ="Immune vs Parasite measure",
    'relevel(factor(precopulatory_postcopulatory_traits), ref = "postcopulatory")' ="Investment type")) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_cor_selectmod 
```

```{r corpselect, tab.cap="Averaged model results from AICc model selection for correlational studies on the relationship between immune function and reproductive investment.", echo = FALSE, messages = FALSE, warning = FALSE}
avg_cor_res<-as.data.frame(summary(avg_cor_RVE)$coefmat.subset)
avg_cor_CI<-as.data.frame(confint(avg_cor_RVE))

avg_cor <- cbind(avg_cor_res,
                           avg_cor_CI)

avg_cor$term <- c("Intercept",
                  "Immune outcome: Induced",
                  "Male competition type: Scramble",
                  "Female mating frequency: Low/monogamous",
                  "Immune vs parasite measure: Parasite")

avg_cor <- avg_cor[, c(7, 1, 2, 3,4,5,6)]

avg_cor[2:7] <- lapply(avg_cor[2:7], as.numeric)

ft_avg_cor <- flextable(avg_cor) %>% 
  set_header_labels(values = list(
    term = "",
    "df" = "df",
    "Pr(>|z|)" ="p value",
    "2.5 %" ="95% CI lower",
    "97.5 %" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_avg_cor 
```

```{r pubbiasimmmanip, tab.cap="Publication bias model results for experiments testing the effect of an immune challenge on reproductive investment.", echo = FALSE, messages = FALSE, warning = FALSE}
pub_bias_imm_manip_RVE_tab <- as.data.frame(coef(summary(robust(pub_bias_imm_manip, cluster=SMD_imm_manip$paperid))))

pub_bias_imm_manip_RVE_tab$term <- c("Intercept",
                  "Parasite type: Endoparasite",
                  "Challenge type: Non-live",
                  "Investment type: Postcopulatory",
                  "Investment type: Precopulatory",
                  "Developmental stage: Juvenile",
                  "Male competition type: Scramble",
                  "√(1/ñ)",
                  "Year of publication")

pub_bias_imm_manip_RVE_tab <- pub_bias_imm_manip_RVE_tab[, c(8, 1, 2, 3,4,5,6,7)]

pub_bias_imm_manip_RVE_tab[2:8] <- lapply(pub_bias_imm_manip_RVE_tab[2:8], as.numeric)

ft_pub_bias_imm_manip_RVE_tab <- flextable(pub_bias_imm_manip_RVE_tab) %>% 
  set_header_labels(values = list(
    term = "",
    "estimate" ="Estimate",
    "se" ="SE",
    "tval" = "t value",
    "df" = "df",
    "pval" ="p value",
    "ci.lb" ="95% CI lower",
    "ci.ub" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_pub_bias_imm_manip_RVE_tab 

```

## Supplementary figures

```{r supfigmodelcheckmanip, warning=FALSE, fig.cap="Moderator multicollinearity check for experimental studies testing the effect of (A) immune challenge on reproductive investment and (B) reproductive investment on immune function using Goodman and Kruskal’s τ association scores between categorical variables.", echo = FALSE, fig.height = 30, fig.width = 60,dpi=300, fig.align = "center"}

colnames(GKmatrix_imm_manip) <- c("Parasite type", 
                                    "Challenge type", 
                                    "Investment type", 
                                    "Developmental stage", 
                                    "Species sexual selection mode",
                                  "Female mating frequency",
                                  "Male competition type",
                                  "Order")

rownames(GKmatrix_imm_manip) <- c("Parasite type", 
                                    "Challenge type", 
                                    "Investment type", 
                                    "Developmental stage", 
                                    "Species sexual selection mode",
                                  "Female mating frequency",
                                  "Male competition type",
                                  "Order")
plot(GKmatrix_imm_manip)

colnames(GKmatrix_repro_manip) <- c("Immune measure type", 
                                    "Female mating frequency", 
                                    "Male competition type", 
                                    "Order")

rownames(GKmatrix_repro_manip) <- c("Immune measure type", 
                                    "Female mating frequency", 
                                    "Male competition type", 
                                    "Order")

plot(GKmatrix_repro_manip)

imm_manip_mod <- magick::image_read_pdf(here("figs2a.pdf"))

imm_manip_mod <- image_annotate(imm_manip_mod, "(A)", size =  10, gravity = "NorthWest", color = "black")

repro_manip_mod <- magick::image_read_pdf(here("figs2b.pdf"))

repro_manip_mod <- image_annotate(repro_manip_mod, "(B)", size =  10, gravity = "NorthWest", color = "black")

comb_mod <- c(imm_manip_mod, repro_manip_mod)

image_append(image_scale(comb_mod, "x2000"))

comb_mod_pdf <-image_append(image_scale(comb_mod, "x2000"))

image_write(comb_mod_pdf , path = "figsupp2.pdf", format = "pdf")


```

```{r supfigmodelcheckcor, warning=FALSE, fig.cap="Moderator multicollinearity check for correlational studies using Goodman and Kruskal’s τ association scores between categorical variables.", echo = FALSE, fig.height = 30, fig.width = 30,dpi=300, fig.align = "center"}
plot(GKmatrix_cor)
colnames(GKmatrix_cor) <- c("Investment type", 
                                    "Immune measure type", 
                                    "Species sexual selection mode", 
                                    "Female mating frequency", 
                                    "Male competition type",
                                  "Order",
                                  "Immune vs parasite measure")

rownames(GKmatrix_cor) <- c("Investment type", 
                                    "Immune measure type", 
                                    "Species sexual selection mode", 
                                    "Female mating frequency", 
                                    "Male competition mode",
                                  "Order",
                                  "Immune vs parasite measure")

cor_mod <- magick::image_read_pdf(here("GKmatrix_cor.pdf"))

image_append(image_scale(cor_mod, "x2000"))

```

## Supplementary results

```{r SMD main moderator with year, echo = FALSE, results = "hide", messages = FALSE}
eval(metafor:::.MuMIn)

keepVars <- c("yi", 
              "vi",
              "paperid",
              "esid",
              "ecto_endo",
                "live_nonlive",
                "precopulatory_postcopulatory_traits",
                "developmental_stage",
                "female_mating_frequency2",
                "contest_scramble",
              "centered_year")

SMD_imm_manip_compl <- SMD_imm_manip[, keepVars] #dataset with these variables only

SMD_imm_manip_compl <- SMD_imm_manip_compl[complete.cases(SMD_imm_manip_compl),] #removes missing values


res_mean_imm_manip_modsel <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          relevel(factor(precopulatory_postcopulatory_traits),ref="precopulatory") +
                          factor(developmental_stage) +
                          factor(female_mating_frequency2) +
                          factor(contest_scramble)+
                          centered_year,
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))

res_mean_imm_manip_modsel_RVE <- robust(res_mean_imm_manip_modsel, cluster = paperid)

summary(res_mean_imm_manip_modsel_RVE)

imm_manip_candidate.models <- dredge(res_mean_imm_manip_modsel)

imm_manip_subset.models_year<- subset(imm_manip_candidate.models, delta < 2)
model.sel(imm_manip_subset.models_year)

#Average models with RVE

mod_imm_manip46 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(developmental_stage)+
                          centered_year,
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))

mod_imm_manip110 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
               mods = ~ relevel(factor(precopulatory_postcopulatory_traits),ref="precopulatory") +
                 factor(developmental_stage) + 
                 factor(live_nonlive)+
                 factor(ecto_endo)+
                          centered_year,
               method="ML",
               data = SMD_imm_manip_compl,
               sparse=T,
               test="t",
                        control=list(optimizer="BFGS"))

mod_imm_manip62 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
               mods = ~ factor(developmental_stage) + 
                 factor(live_nonlive)+
                 factor(ecto_endo)+
                          factor(female_mating_frequency2)+
                          centered_year,
               method="ML",
               data = SMD_imm_manip_compl,
               sparse=T,
               test="t",
                        control=list(optimizer="BFGS"))



mod_imm_manip42 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(live_nonlive)+
                 factor(ecto_endo)+
                          centered_year,
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))



mod_imm_manip48 <- rma.mv(yi=yi, V=vi,
                                    random= list(~1|paperid,~1|esid),
                        mods = ~ factor(ecto_endo)+
                          factor(live_nonlive)+
                          factor(developmental_stage) +
                          factor(contest_scramble)+
                          centered_year,
                        method="ML",
                        sparse=T,
                        data = SMD_imm_manip_compl,
                        test = "t",
                        control=list(optimizer="BFGS"))



mod_imm_manip46_RVE <- robust(mod_imm_manip46, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip42_RVE <- robust(mod_imm_manip42, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip62_RVE <- robust(mod_imm_manip62, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip110_RVE <- robust(mod_imm_manip110, cluster = SMD_imm_manip_compl$paperid)
mod_imm_manip48_RVE <- robust(mod_imm_manip48, cluster = SMD_imm_manip_compl$paperid)

modsel_imm_manip_RVE_year<- model.sel(mod_imm_manip46_RVE,
                   mod_imm_manip42_RVE,
                   mod_imm_manip62_RVE,
                   mod_imm_manip110_RVE,
                   mod_imm_manip48_RVE,
                   rank = "AICc")

avg_imm_manip_RVE_year <- model.avg(modsel_imm_manip_RVE_year)

summary(avg_imm_manip_RVE_year)
confint(avg_imm_manip_RVE_year)

#For reproduction manipulation studies
keepVars_repro <- c("yi", 
              "vi",
              "paperid",
              "esid",
              "female_mating_frequency2",
                "contest_scramble",
                "constitutive_induced",
              "centered_year")

SMD_repro_manip_compl <- SMD_repro_manip[, keepVars_repro] #dataset with these variables only

SMD_repro_manip_compl <- SMD_repro_manip_compl[complete.cases(SMD_repro_manip_compl),] #removes missing values

res_mean_repro_manip_modsel <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(female_mating_frequency2) +
                          factor(contest_scramble)+
                          factor(constitutive_induced)+
                          centered_year,
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

repro_manip_candidate.models <- dredge(res_mean_repro_manip_modsel)

repro_manip_subset.models_year<- subset(repro_manip_candidate.models, delta < 2)
model.sel(repro_manip_subset.models_year)

#Average models with RVE

mod_repro_manip2 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ centered_year,
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip4 <- rma.mv(yi=yi, V=vi,
                        random= list(~1|paperid,~1|esid),
                        mods = ~ factor(constitutive_induced)+
                          centered_year,
                        method="ML",
                        data = SMD_repro_manip_compl,
                        sparse=T,
                        test="t",
                        control=list(optimizer="BFGS"))

mod_repro_manip2_RVE <- robust(mod_repro_manip2, cluster = SMD_repro_manip_compl$paperid)
mod_repro_manip4_RVE <- robust(mod_repro_manip4, cluster = SMD_repro_manip_compl$paperid)

modsel_repro_manip_RVE_year<- model.sel(mod_repro_manip2_RVE,
                   mod_repro_manip4_RVE,
                   rank = "AICc")

avg_repro_manip_RVE_year <- model.avg(modsel_repro_manip_RVE_year)

summary(avg_repro_manip_RVE_year)
confint(avg_repro_manip_RVE_year)
```

```{r immmanipmodelsyear, tab.cap="AICc model selection table for experiments that tested the effect of an immune challenge on reproductive investment repeated with year of publication included. Models presented are those that were within 2 AICc points from the best fit model.", echo = FALSE, messages = FALSE, warning = FALSE}
imm_manip_selectmod_year <- as.data.frame(model.sel(imm_manip_subset.models_year))

ft_imm_manip_selectmod_year <- flextable(imm_manip_selectmod_year) %>% 
  set_header_labels(values = list(
    "(Intercept)" = "Intercept",
    "centered_year" = "Year of publication",
    "factor(contest_scramble)" ="Male competition type",
    "factor(developmental_stage)" ="Developmental stage",
    "factor(ecto_endo)" ="Parasite type",
    "factor(female_mating_frequency2)" ="Female mating frequency",
    "factor(live_nonlive)" ="Challenge type",
    'relevel(factor(precopulatory_postcopulatory_traits), ref = "precopulatory")' ="Investment type")) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_imm_manip_selectmod_year 
```

```{r supimmmanipselect, tab.cap="Averaged model results from AICc model selection for experiments that tested the effects of an immune challenge on reproductive investment repeated with year of publication included as a potential moderator.", echo = FALSE, messages = FALSE, warning = FALSE}
avg_imm_manip_year_res<-as.data.frame(summary(avg_imm_manip_RVE_year)$coefmat.subset)
avg_imm_manip_year_CI<-as.data.frame(confint(avg_imm_manip_RVE_year))

avg_imm_manip_year <- cbind(avg_imm_manip_year_res,
                           avg_imm_manip_year_CI)

avg_imm_manip_year$term <- c("Intercept",
                  "Parasite type:Endoparasite",
                  "Challenge type:Non-live",
                  "Developmental stage: Juvenile",
                  "Year of publication",
                  "Investment type: Pre- and Post-",
                  "Investment type: Post-mating",
                  "Female mating frequency: Monogamous/Low",
                  "Male competition type: Scramble")

avg_imm_manip_year <- avg_imm_manip_year[, c(7, 1, 2, 3,4,5,6)]

avg_imm_manip_year[2:7] <- lapply(avg_imm_manip_year[2:7], as.numeric)

ft_avg_imm_manip_year <- flextable(avg_imm_manip_year) %>% 
  set_header_labels(values = list(
    term = "",
    "df" = "df",
    "Pr(>|z|)" ="p value",
    "2.5 %" ="95% CI lower",
    "97.5 %" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_avg_imm_manip_year 
```

```{r repromanipmodelsyear, tab.cap="AICc model selection table for experiments that tested the effect of reproductive investment on immune function repeated with year of publication included. Models presented are those that were within 2 AICc points from the best fit model.", echo = FALSE, messages = FALSE, warning = FALSE}
repro_manip_selectmod_year <- as.data.frame(model.sel(repro_manip_subset.models_year))

ft_repro_manip_selectmod_year <- flextable(repro_manip_selectmod_year) %>% 
  set_header_labels(values = list(
    "(Intercept)" = "Intercept",
    "centered_year" = "Year of publication",
    "factor(constitutive_induced)" = "Immune outcome")) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_repro_manip_selectmod_year
```

```{r suprepromanipselect, tab.cap="Averaged model results from AICc model selection for experiments that tested the effects of reproductive investment on immune function repeated with year of publication included as a potential moderator.", echo = FALSE, messages = FALSE, warning = FALSE}
avg_repro_manip_year_res<-as.data.frame(summary(avg_repro_manip_RVE_year)$coefmat.subset)
avg_repro_manip_year_CI<-as.data.frame(confint(avg_repro_manip_RVE_year))

avg_repro_manip_year <- cbind(avg_repro_manip_year_res,
                           avg_repro_manip_year_CI)

avg_repro_manip_year$term <- c("Intercept",
                  "Year of publication",
                  "Immune outcome: Induced")

avg_repro_manip_year <- avg_repro_manip_year[, c(7, 1, 2, 3,4,5,6)]

avg_repro_manip_year[2:7] <- lapply(avg_repro_manip_year[2:7], as.numeric)

ft_avg_repro_manip_year <- flextable(avg_repro_manip_year) %>% 
  set_header_labels(values = list(
    term = "",
    "df" = "df",
    "Pr(>|z|)" ="p value",
    "2.5 %" ="95% CI lower",
    "97.5 %" ="95% CI upper")) %>% 
  colformat_double(digits = 2) %>% 
  flextable::align(part = "body", align = "center") %>% 
  flextable::align(j = 1, align = "left") %>% 
  flextable::font(fontname='Times New Roman', part ="all") %>% 
  flextable::autofit()

ft_avg_repro_manip_year
```

